### 2020-06-16 paper/Paper.Rmd
Updates to examples and the formatting of the column names in the output of PoolPrev

---
title: "PoolTestRPaper"
author: "AngusMcLure"
date: "05/06/2020"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The PoolTestR package [Angus]
The `PoolTestR` package has been designed to be a simple, fast, and user-friendly way to work with data from pooled samples of insects or other specimens. The package has two primary functions. `PoolPrev` estimates the prevalence of a marker based on the outcome of tests on pooled samples, calculating prevalence for many subgroups of the dataset if desired. `PoolLogitReg` fits a logistic regression model modified to account for the size of pools, allowing users to identify temporal trends or variables (e.g. altitude, population density, interventions) associated with higher prevalence. 
`PoolPrev` was designed to produce comparable results to the popular stand-alone application PoolScreen for familiarity to existing users of the software. However, PoolScreen requires many manual steps to import data, run analyses, and export results and lacks the flexibility of a general-purpose statistical environment like `R`. Using PoolPrev users can estimate the prevalence of a marker for their whole dataset or for many different subgroups of their data (e.g. by vector species, location, season, or the combination of all variables) with a few lines of `R` code and simple syntax. This is achieved by utilising non-standard evaluation and tools for working with grouped datasets provided in the `R` package, `dplyr`. `PoolLogitReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for familiarity to `R` users and to leverage the diagnostics from `glm`.

### PoolPrev
Given a dataset containing the number of samples and the result of tests for each pool, `PoolPrev` returns Bayesian and maximum likelihood estimates of the prevalence together with uncertainty intervals. Efficient Bayesian inference is performed with Hamiltonian Markov Chain Monte Carlo using the Stan programming language and the `rstan` package. Users can specify their prior belief for the prevalence from the Beta distribution, or use the uninformative 'Jefferey's' prior i.e. Beta(0.5,0.5). Users can also optionally specify the prior probability that the marker of interested is entirely absent from the population, in which case `PoolPrev` also returns the probability of absence given the data. As we assume the test performed on the pooled samples does not produce false positive or negatives, the probability of absence is always zero if any of the pools test positive. In most cases the credible interval (CrI) for the prevalence are the 2.5% and 97.5% quantiles of the posterior distribution. However, if all tests are positive the upper bound of the CrI is 1 and the lower bound is the 5% quantile of the posterior. Similarly, if all tests are negative the lower bound of the CrI is 0 and the lower bound is the 95% quantile of the posterior.
The maximum likelihood estimate is calculated using the `optimizing` function from the `rstan` package. The uncertainty interval for the maximum likelihood estimate is calculated using the likelihood ratio method (i.e. a Wilk’s confidence interval) using the `uniroot` function from the `stats` package. As with the Bayesian credible interval, the lower or upper bound of the confidence intervals are zero or one when all pools are negative or positive, respectively.

The boxes below demonstrated the use of `PoolPrev` on a synthetic dataset. The synthetic dataset consists of 1000 pools from four different locations (A-D) over five years (0-4) of sampling. The ‘true’ prevalence in the initial year was 14% in locations A and D, 4% in location B and 1% in location C, and declined by approximately 18% each year.

```{r buildpackage, include=FALSE}
pkgbuild::compile_dll()
roxygen2::roxygenize()

```

```{r GenerateDataset, include=FALSE}
### Create a synthetic dataset with 4 locations across 5 years,
### where prevalence is declining
NumPools <- 1000
#Odds that a individual sample is positive in each location in the first year
BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
OddsRatioYear <- 0.8
#Randomly distribute pools between the 4 locations and 5 years,
#and chose random pool sizes between 10 and 25
Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
                   Year = sample(c(0:4), NumPools, replace = T),
                   NumInPool = sample(10:25, NumPools, replace = T))
#'True' odds/prevalence in each location
Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
#Simulate test results on pools
Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
library(dplyr)
Data <- Data %>% select(-TrueOdds,-TruePrev)
```

```{r PoolPrevExample}
#Looking at the first few rows of the synthetic dataset to see structure
head(Data)
#Prevalence across the whole synthetic dataset
PoolPrev(Data, Result,NumInPool)
#Prevalence at each location
PoolPrev(Data, Result,NumInPool,Place)
#Prevalence for each Year
PoolPrev(Data, Result,NumInPool,Year)
#Prevalence for each combination of location and Year
PoolPrev(Data, Result,NumInPool,Place,Year)
```

### PoolLogitReg
Given a dataset containing the number of samples, the result of tests for each pool, potential dependent variables associated with each pool, and a formula defining the model, `PoolLogitReg` fits a logistic regression model that adjusts for the sizes of pools. The output is a S3-object of class `glm` which supports that same methods (e.g. summary, predict, plot, confint) as any other object returned by the `glm` function.

The boxes below apply `PoolLogitReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.

```{r PoolLogitRegExample}
# Fit modified logistic regression model
#The below two lines produce identical results and support all the same methods
Reg <- PoolLogitReg(Data,
                    Result ~ Place + Year,
                    NumInPool)
Reg.glm <- glm(Result ~ Place + Year,
               data = Data,
               family = binomial(PoolLink(Data$NumInPool)))
#View summary of model
summary(Reg)

#Estimate and confidence intervals for the base odds and odds ratios
#These should be approx 0.16 for the intercept (i.e. Place A, Year 0),
#0.25, 0.0625, and 1.0 for places B-D and 0.8 for Year
exp(cbind(Estimate = coefficients(Reg), confint(Reg)))

#You can use the fitted model to predict the prevalence at other times
#The times and places at which to predict the prevalence
DataPredict <- expand.grid(Place = c("A","B","C","D"),Year = seq(2.2,2.8,by = 0.2))
#Predicted prevalence
DataPredict$PredictPrev <- plogis(predict(Reg, newdata = DataPredict)) 
head(DataPredict)

# Note that predicting the response (i.e. the predicting the probability of
# observing a positive test) using predict(type = "response") does not work
# as expected on new data. Use the following instead:

#Generate new random pool sizes for new data
DataPredict$NumInPool <- sample(5:10,nrow(DataPredict),replace = T)
DataPredict$PredictTestProb <- with(DataPredict, 1 - (1-PredictPrev)^NumInPool)
head(DataPredict)
```

Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolPrevLogit`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location. Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
```{r Comparison, echo=FALSE}
library(ggplot2)
PrevsYearPlace <- PoolPrev(Data, Result,NumInPool,Place,Year)
PO <- PrevsYearPlace %>%
  mutate(BaseOdds = BaseOdds[Place],
         TrueOdds = BaseOdds * OddsRatioYear^(Year-min(Year)),
         TruePrev = TrueOdds/(1+TrueOdds),
         FreqPred = plogis(predict(Reg,newdata = PrevsYearPlace)),
         FreqPredCILow = with(predict(Reg,
                                      newdata = PrevsYearPlace,
                                      se.fit =T),
                              fit - se.fit * 1.96) %>% plogis,
         FreqPredCIHigh = with(predict(Reg,
                                       newdata = PrevsYearPlace,
                                       se.fit =T),
                               fit + se.fit * 1.96) %>% plogis
  ) %>%
  ggplot() +
  geom_pointrange(aes(x = Year,
                      color = Place,
                      y = PrevMLE,
                      ymin = CILow,
                      ymax = CIHigh)) +
  geom_line(aes(x = Year,
                y= FreqPred,
                color = Place)) +
  geom_ribbon(aes(x = Year,
                  ymin = FreqPredCILow,
                  ymax = FreqPredCIHigh,
                  fill = Place),
              alpha = 0.3) +
  geom_point(aes(x = Year, color = Place, y = TruePrev),
             shape = 4,
             size = 3) +
  #scale_y_log10() +
  ylab('Prevalence')
PO
```

### 2020-06-16 R/PoolTestR.R

@@ -24,10 +24,10 @@
 #' @param verbose Logical indicating whether to print progress to screen. Defaults to false (no printing to screen)
 #' @return A \code{data.frame} with columns:
 #' \itemize{
-#'  \item{\code{MLE} (the Maximum Likleihood Estimate of prevelance)}
-#'  \item{\code{LR-CI Lower} and \code{LR-CI Upper} (Lower and Upper Confidence intervals using the Likelihood Ratio method)}
+#'  \item{\code{PrevMLE} (the Maximum Likleihood Estimate of prevelance)}
+#'  \item{\code{CILow} and \code{CIHigh} (Lower and Upper Confidence intervals using the Likelihood Ratio method)}
 #'  \item{\code{Bayesian Posterior Expectation}}
-#'  \item{\code{Bayesian CI Lower} and \code{Bayesian CI Upper}}
+#'  \item{\code{CrILow} and \code{CrIHigh}}
 #'  \item{\code{Number of Pools}}
 #'  \item{\code{Number Positive}}
 #' }
@@ -42,13 +42,13 @@
 #'                    NumInPool = sample(1:10,1000, replace = TRUE),
 #'                    Result = sample(0:1,1000,replace = TRUE)
 #'                    )
-#' #Prevalence across the whole (fake) dataset
+#' #Prev across the whole (fake) dataset
 #' PoolPrev(Data, Result,NumInPool)
-#' #Prevalence at each location
+#' #Prev at each location
 #' PoolPrev(Data, Result,NumInPool,Place)
-#' #Prevalence for each time period
+#' #Prev for each time period
 #' PoolPrev(Data, Result,NumInPool,Date)
-#' #Prevalence for each combination of location and time period
+#' #Prev for each combination of location and time period
 #' PoolPrev(Data, Result,NumInPool,Place,Date)
 
 PoolPrev <- function(data,TestResult,PoolSize,...,
@@ -82,7 +82,7 @@ PoolPrev <- function(data,TestResult,PoolSize,...,
     sfit <- sampling(stanmodels$BayesianPoolScreen,
                      data = sdata,
                      pars = c('p'),
-                     chains = 1,
+                     chains = 4,
                      iter = 2000,
                      warmup = 1000,
                      refresh = ifelse(verbose,200,0),
@@ -100,8 +100,8 @@ PoolPrev <- function(data,TestResult,PoolSize,...,
     #Calculate the Maximum likelihood estimate -- this is exactly zero if all the pools are negative and exactly one if all are positive
[…]

### 2020-06-16 examples/LogisticRegression.R

@@ -1,47 +1,52 @@
-#Simulated data with the same trend but different baselines in every place
-N <- 1000
-DataTrend <- data.frame(Place = sample(c("A","B","C","D"),N, replace = T),
-                        Year = sample(c(0:2), N, replace = T),
-                        NumInPool = sample(1:100, N, replace = T)
-)
-BaseOdds <- c(A = 0.1, B = 0.05, C = 0.002, D = 0.1)
-GrowthRate = -0.5 #This is equivalent to an odds ratio for year of exp(-0.5) = 0.6065
-DataTrend$TrueOdds <- with(DataTrend,BaseOdds[Place] * exp(GrowthRate*(Year-min(Year))))
-DataTrend$TruePrev <- with(DataTrend, TrueOdds/(1+TrueOdds))
-DataTrend$Result <- with(DataTrend,as.numeric(runif(N) < 1-(1-TruePrev)^NumInPool))
+### Create a simulated dataset with 4 locations across 5 years, where prevalence is declining
+NumPools <- 1000
+#Odds that individual sample is positive in each location in the first year
+BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+OddsRatioYear <- 0.8
+#Randomly distribute pools between the 4 locations and 5 years,
+#and chose random pool sizes between 10 and 25
+Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
+                   Year = sample(c(0:4), NumPools, replace = T),
+                   NumInPool = sample(10:25, NumPools, replace = T))
+#'True' odds/prevalence in each location
+Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
+Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
+#Simulate test results on pools
+Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
+
+### Fit modified logistic regression model
 
 #The below two lines produce identical results and support all the same methods
-Reg <- PoolLogitReg(DataTrend,
+Reg <- PoolLogitReg(Data,
                     Result ~ Place + Year,
                     NumInPool)
 Reg.glm <- glm(Result ~ Place + Year,
-               data = DataTrend,
-               family = binomial(PoolLink(DataTrend$NumInPool)))
+               data = Data,
+               family = binomial(PoolLink(Data$NumInPool)))
 #View summary of model
 summary(Reg)
 
[…]

### 2020-06-16 test/PooledRegressionExamples.R

@@ -1,53 +1,92 @@
-#Fake data with no trend
-pkgbuild::compile_dll(force =T)
 pkgbuild::compile_dll()
 roxygen2::roxygenize()
-devtools::check()
 
-N <- 200
+### Create a simulated dataset with 4 locations across 5 years, where prevalence is declining
+NumPools <- 1000
+#Odds that individual sample is positive in each location in the first year
+BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+OddsRatioYear <- 0.8
+#Randomly distribute pools between the 4 locations and 5 years,
+#and chose random pool sizes between 10 and 25
+Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
+                   Year = sample(c(0:4), NumPools, replace = T),
+                   NumInPool = sample(10:25, NumPools, replace = T))
+#'True' odds/prevalence in each location
+Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
+Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
+#Simulate test results on pools
+Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
 
-Data <- data.frame(Place = sample(c("A","B","C","D"),N, replace = T),
-                   Year = sample(c(2000,2001,2002),N, replace = T),
-                   NumInPool = sample(10:30,N, replace = T),
-                   Result = sample(0:1,N,replace = T)
-                   )
+### Fit modified logistic regression model
 
-#Simulated data with the same trend but different baselines in every place
+#The below two lines produce identical results and support all the same methods
+Reg <- PoolLogitReg(Data,
+                    Result ~ Place + Year,
+                    NumInPool)
+Reg.glm <- glm(Result ~ Place + Year,
+               data = Data,
+               family = binomial(PoolLink(Data$NumInPool)))
+#View summary of model
+summary(Reg)
 
-DataTrend <- data.frame(Place = sample(c("A","B","C","D"),N, replace = T),
-                        Year = sample(c(0:2), N, replace = T),
-                        NumInPool = sample(10:25, N, replace = T)
-                        )
-BaseOdds <- c(A = 0.1, B = 0.05, C = 0.002, D = 0.1)
[…]

### 2020-06-16 R/PoolPrev.R
Spilt off examples for PoolPrev into it's own file

@@ -35,21 +35,8 @@
 #' When there are no grouping variables (supplied in \code{...}) then the dataframe has only one row with the prevalence estimates for the whole dataset.
 #' When grouping variables are supplied, then there is a seperate row for each group.
 #'
-#' @examples
-#' #Build a fake dataset with 1000 pools taken from 4 different locations and 3 different times
-#' Data <- data.frame(Place = sample(c("A","B","C","D"),1000, replace = TRUE),
-#'                    Date = sample(as.Date(c("2000/1/1","2001/1/1","2002/1/1")),1000, replace = TRUE),
-#'                    NumInPool = sample(1:10,1000, replace = TRUE),
-#'                    Result = sample(0:1,1000,replace = TRUE)
-#'                    )
-#' #Prev across the whole (fake) dataset
-#' PoolPrev(Data, Result,NumInPool)
-#' #Prev at each location
-#' PoolPrev(Data, Result,NumInPool,Place)
-#' #Prev for each time period
-#' PoolPrev(Data, Result,NumInPool,Date)
-#' #Prev for each combination of location and time period
-#' PoolPrev(Data, Result,NumInPool,Place,Date)
+#' @example examples/Prevalence.R
+
 
 PoolPrev <- function(data,TestResult,PoolSize,...,
                      prior.alpha = 0.5, prior.beta = 0.5, prior.absent = 0,

### 2020-06-16 examples/Prevalence.R

@@ -1,0 +1,14 @@
+#Build a synthetic dataset with 1000 pools taken from 4 different locations and 3 different times
+Data <- data.frame(Place = sample(c("A","B","C","D"),1000, replace = TRUE),
+                   Date = sample(as.Date(c("2000/1/1","2001/1/1","2002/1/1")),1000, replace = TRUE),
+                   NumInPool = sample(1:10,1000, replace = TRUE),
+                   Result = sample(0:1,1000,replace = TRUE)
+)
+#Prevalence across the whole (synthetic) dataset
+PoolPrev(Data, Result, NumInPool)
+#Prevalence at each location
+PoolPrev(Data, Result, NumInPool, Place)
+#Prevalence for each time period
+PoolPrev(Data, Result, NumInPool, Date)
+#Prevalence for each combination of location and time-period
+PoolPrev(Data, Result, NumInPool, Place, Date)

### 2020-06-18 paper/Paper.Rmd
Added a new simulation to the examples for the paper

@@
 ```
+
+## Testing
+A more realistic example:
+- 3 regions with prevalence:
+  - low (0.5%)
+  - medium (2%)
+  - high (4%) 
+- 10 villages in each region with prevalence:
+  - random normal distribted tight around region average, or 
+  - one hotspot and one coldspot village
+- 15 sites at each village.
+  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
+  - Mosquitos pooled into test-tubes of 25 + one pool with remainder
+
+```{r GenerateMoreRealisticDataset}
+RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
+NumRegions <- length(RegionPrevs)
+NumVillages <- 10 #Villages per Region
+NumSites <- 15 #Sites per village
+MeanCatch <- 100; SDCatch <- 30 #Mean and SD of mosquito catch sizes
+DispersionCatch <- 1.5
+#expand.grid(1:NumSites,1:NumVillages,names(RegionPrevs))
+#Catches <- data.frame(Catch = rnorm(NumRegions * NumVillages * NumSites, MeanCatch,sd = SDCatch))
+Data <- data.frame()
+for(R in names(RegionPrevs)){
+  for(V in 1:NumVillages){
+    VillageTruePrev <- 0
+    while(VillageTruePrev<=0){
+      VillageTruePrev <- rnorm(1,mean = RegionPrevs[[R]],sd = RegionPrevs[[R]]/5)
+    }
+    for(S in 1:NumSites){
+      SiteTruePrev <- 0
+      while(SiteTruePrev<=0){
+        SiteTruePrev <- rnorm(1,mean = VillageTruePrev,sd = VillageTruePrev/5)
+      }
+      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes <= 0 to guarantee at least one mossie
+      Catch <- 0
+      while(Catch<=0){
+        Catch <- rnbinom(1,mu = MeanCatch,DispersionCatch)
+      }
+      NumBigPools <- Catch %/% MaxPoolSize
+      if(NumBigPools){
+        Data <- rbind(Data,
+                      data.frame(Region = R,
+                                 Village = paste(R,V,sep = "-"),
+                                 Site = paste(R,V,S,sep = "-"),
+                                 PoolSize = rep(MaxPoolSize,NumBigPools),
+                                 PrevalenceSite = SiteTruePrev,
+                                 PrevalenceVillage = VillageTruePrev,
+                                 PrevalenceRegion = RegionPrevs[[R]]))
+      }
+      SizeSmallPool <- Catch %% MaxPoolSize
+      if(SizeSmallPool){
+        Data <- rbind(Data,
+                      data.frame(Region = R,
+                                 Village = paste(R,V,sep = "-"),
+                                 Site = paste(R,V,S,sep = "-"),
+                                 PoolSize = SizeSmallPool,
+                                 PrevalenceSite = SiteTruePrev,
+                                 PrevalenceVillage = VillageTruePrev,
+                                 PrevalenceRegion = RegionPrevs[[R]]))
+      }
+
+    }
+  }
+}
+Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < 1-(1-PrevalenceSite)^PoolSize))
+
+PrevAll <- PoolPrev(Data,Result,PoolSize)
+PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
+PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
+PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)
+
+```

### 2020-08-13 paper/Paper.Rmd
Added hierarchical models
Also renamed and reorganised quite a lot

--- 2020-06-16 paper/Paper.Rmd
@@
 
+[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen]
+
+We wish to estimate the prevalence, p, of a disease or molecular marker in a population from the results of tests on a pooled samples.
+For a pool combining N samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$.
+If $M$ such pools from a single location are tested and $m$ of these are positive the maximum likelihood estimate (MLE) of $q\ is \frac{m}{M}$ and the MLE of the prevalence, $p$, in the population is ${1-\left(1-\frac{m}{M}\right)}^\frac{1}{N}$.
+However, if the pools are of different sizes there is no convenient closed-form expression for the MLE, which must be approximated numerically from the likelihood function.
+With pools of size $N_1,N_2,\ldots$, and tests results $y_1,y_2,\ldots$ (where $y_i$ is zero if the test result is negative and one if positive) the likelihood function is
+
+$L\left(p\middle|y\right)=\prod_{i}{y_i+\left(-1\right)^{y_i}\ \left(1-p\right)^{N_i}}.$
+
+Similarly, Bayesian inference has to performed numerically in most cases.
+However, in the special case where all pool tests are negative and the prior on $p$ has a $Beta(\alpha,\beta)$ distribution, the posterior for $p$ is given by $Beta(\alpha,\beta+\sum_{i}\ N_i)$.
+In some locations there may be some reasonable prior probability that the disease is absent i.e.
+prevalence is exactly zero.
+Thus, we may wish to consider a prior such that $p$ has probability $\gamma$ of being exactly zero and $Beta(\alpha,\beta)$ distributed otherwise.
+If any test results are positive then the posterior probability of absence is zero and the posterior distribution of $p$ is the same as would be reached with an unmodified $Beta(\alpha,\beta)$ prior.
+However, in the case where all test results are negative
+
+$P\left(p=0|y=0,N\right)=\left(1+\frac{\left(1-\gamma\right)B\left(\alpha,\beta+\sum_{i}\ N_i\right)}{\gamma B\left(\alpha,\ \beta\right)}\right)^{-1}$,
+
+where $B(.,.)$ is the beta function.
+
+Prevalence may vary over the different locations, times, and subpopulation from which the samples are taken, so we may wish to use regression analyses model the relationship between prevalence and a set of explanatory variables recorded for each pool.
+We use a logistic regression model adjusted for pool sizes which can be viewed as a kind of generalised linear model.
+Mathematically, our modified logisitic model is similar to Shaffer’s model of bird nesting success rates, which adjusts the logistic model to account for different durations of nest observations (Shaffer, T.
+2004.
+Auk 121(2): 526-540).
+Let $x_{ij}$ be the observed value of dependent variable $j$ for pool $i$ and $x_{i0}=1$.
+A standard unadjusted logistic regression model with intercept $\beta_0$ and parameters $\beta_j$ would model test results as
+
+$y_i |\beta, x_{ij} \sim Bernoulli( logit^{-1} \sum_{j}{x_{ij} \beta_j} )$.
+
+However, with pooled samples we model the results of pooled tests as
+$y_i |\beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1} \sum_{j}{x_{ij} \beta_j} \right)^{N_i}\right)$.
+
+When all pool sizes are one, this simplifies to the standard logistic model. Maximum likelihood estimation and Bayesian inference must be performed numerically from the likelihood function:
+
+$L\left(\beta\middle|y,x,N\right)=\prod_{i}{y_i+\left(-1\right)^{y_i}\ \left(1-logit^{-1}\sum_{j}{x_{ij}\beta_j}\right)^{N_i}}$.
+
+It is common to adopt a hierarchical sampling structure when collecting specimens.
+For instance, if one wishes to estimate the prevalence of a marker in mosquitos,  a common way to collect specimens is to set out mosquito traps.
+To estimate the typical prevalence in a region, one may place traps in a number of randomly or systemtically chosen sites.
+In such cases it would be best to attempt to account for any intra-site variation in prevalence using a hiearachical or mixed-effects modelling framework.
+In the general case let $z_{ik}$ define the design matrix and $u_k$ the group effects for a mixed-effects model.
+Then we model the outcomes as
+
+$y_{i} |u, z_{ik},\beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1}\left(\sum_{k}{z_{ik} u_k} + \sum_{j}{x_{ij} \beta_j}\right) \right)^{N_i}\right)$
+
+$u \sim N(0, \Sigma)$.
+
+For the more specific case of a $K$-level hierarchical model where group membership only influences the intercept, let $y_{is}$ be the result of pool $i$ taken from site $s$, where $s_1, \dots, s_K$ give the group memberhsip at levels $1,\dots, K$ of the hierarchical sampling scheme.
+Let $u_g^k$ be the group effect for group $g$ from level $k$ of the sampling scheme.
+Then our model is
+
+$y_{i s} |u_{s_k}^1,\dots,u_{s_k}^K, \beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1}\left(\sum_k u^k_{s_k} + \sum_{j}{x_{ij} \beta_j}\right) \right)^{N_i}\right)$.
+
+$u^k_g \sim N(0,\sigma_k^2)$.
+
 ## The PoolTestR package [Angus]
 The `PoolTestR` package has been designed to be a simple, fast, and user-friendly way to work with data from pooled samples of insects or other specimens.
-The package has two primary functions.
+The package has four primary functions.
 `PoolPrev` estimates the prevalence of a marker based on the outcome of tests on pooled samples, calculating prevalence for many subgroups of the dataset if desired.
-`PoolLogitReg` fits a logistic regression model modified to account for the size of pools, allowing users to identify temporal trends or variables (e.g.
-altitude, population density, interventions) associated with higher prevalence.
-`PoolPrev` was designed to produce comparable results to the popular stand-alone application PoolScreen for familiarity to existing users of the software.
-However, PoolScreen requires many manual steps to import data, run analyses, and export results and lacks the flexibility of a general-purpose statistical environment like `R`.
-Using PoolPrev users can estimate the prevalence of a marker for their whole dataset or for many different subgroups of their data (e.g.
-by vector species, location, season, or the combination of all variables) with a few lines of `R` code and simple syntax.
+`HierPoolPrev` is like `PoolPrev`  but allows users to adjust prevalence estimates for hierarchical structure in sampling frames.
+`PoolReg` and `PoolRegBayes` fit mixed or fixed effect logistic regression models modified to account for the size of pools in either a frquentist or a bayesian framework.
+These allow users to identify temporal trends or variables (e.g.
+altitude, population density, interventions) associated with higher prevalence and to account for hierarchical sampling designs when estimating prevalence[^1].
+
+`PoolPrev` was designed to produce comparable results to the popular stand-alone application PoolScreen [ref Katholi1996] for familiarity to existing users of the software.
+However, PoolScreen requires many manual steps to import data, run analyses, and export results and lacks the flexibility of a general-purpose statistical environment provided by `R`.
+Using `PoolPrev` users can estimate the prevalence of a marker for their whole dataset or for different subgroups of their data (e.g.
+splitting data by vector species, location, season, or the combination of all variables) with a few lines of `R` code and simple syntax.
 This is achieved by utilising non-standard evaluation and tools for working with grouped datasets provided in the `R` package, `dplyr`.
-`PoolLogitReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for familiarity to `R` users and to leverage the diagnostics from `glm`.
+`HierPoolPrev` uses the same syntax as `PoolPrev` and returns results in a similar format, but allows users to adjust estimates of prevalence to account for the hierarchical sampling frame often employed in xenomonitoring studies.
+
+ `PoolReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for fixed effects models and builds on the `glmer` function from the `lme4` package for mixed effect models.
+`PoolRegBayes` builds on the flexible non-linear modelling framework provided by the `brms` package to fit bayesian fixed and mixed effect regression models on data from pooled tests.
+By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of R.
+
+[^1]: example of people doing this - though it's not clear what model/software they used: Subramanian-2020-Molecular xenomonitoring as a post-MDA surveillance tool for global programme to eliminate lymphatic filariasis- Field validation in an evaluation unit in India
 
 ### PoolPrev
+
 Given a dataset containing the number of samples and the result of tests for each pool, `PoolPrev` returns Bayesian and maximum likelihood estimates of the prevalence together with uncertainty intervals.
@@
 Users can specify their prior belief for the prevalence from the Beta distribution, or use the uninformative 'Jefferey's' prior i.e.
-Beta(0.5,0.5).
+$Beta(0.5,0.5)$.
 Users can also optionally specify the prior probability that the marker of interested is entirely absent from the population, in which case `PoolPrev` also returns the probability of absence given the data.
@@
 
-```{r buildpackage, include=FALSE}
-pkgbuild::compile_dll()
-roxygen2::roxygenize()
-
-```
-
 ```{r GenerateDataset, include=FALSE}
+library(dplyr)
+library(tidyr)
 ### Create a synthetic dataset with 4 locations across 5 years,
@@
 Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
-library(dplyr)
 Data <- Data %>% select(-TrueOdds,-TruePrev)
@@
 #The below two lines produce identical results and support all the same methods
-Reg <- PoolLogitReg(Data,
-                    Result ~ Place + Year,
+Reg <- PoolReg(Data,Result ~ Place + Year,
                     NumInPool)
@@
 
-Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolPrevLogit`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location.
+Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolReg`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location.
 Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
@@
 ```
+
+## Testing
+A more realistic example:
+- 3 regions with prevalence:
+  - low (0.5%)
+  - medium (2%)
+  - high (4%) 
+- 10 villages in each region with prevalence:
+  - random normal distribted tight around region average, or 
+  - one hotspot and one coldspot village
+- 15 sites at each village.
+  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
+  - Mosquitos pooled into test-tubes of 25 + one pool with remainder
+
+```{r GenerateMoreRealisticDataset}
+RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
+NumRegions <- length(RegionPrevs)
+NumVillages <- 10 #Villages per Region
+NumSites <- 15 #Sites per village
+MeanCatch <- 200; #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
+DispersionCatch <- 5
+MaxPoolSize <- 25
+# Variability between villages and between sites in a given village.
+# We could probably increase these standard deviations to make the difference between the hierarchical and non-hierarchical models more stark
+VillageSD <- 1.0 
+SiteSD <- 0.5
+
+Data <- data.frame()
+for(R in names(RegionPrevs)){
+  for(V in 1:NumVillages){
+    #Difference of village prevalence from the region prevalence on log-odds scale
+    VillageDeviate <- rnorm(1,mean = 0, sd = VillageSD)
+    VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate)
+    for(S in 1:NumSites){
+      #Difference of site prevalence from the village prevalence on log-odds scale
+      SiteDeviate <- rnorm(1,mean = 0, sd = SiteSD)
+      SiteTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + SiteDeviate)
+      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes == 0 to guarantee at least one mossie
+      Catch <- 0
+      while(Catch<=0){
+        Catch <- rnbinom(1,mu = MeanCatch ,DispersionCatch)
+      }
+      #Split pools into as many of size MaxPoolSize as possible and the remainder in another small pool
+      NumBigPools <- Catch %/% MaxPoolSize
+      if(NumBigPools){
+        Data <- rbind(Data,
+                      data.frame(Region = R,
+                                 Village = paste(R,V,sep = "-"),
+                                 Site = paste(R,V,S,sep = "-"),
+                                 PoolSize = rep(MaxPoolSize,NumBigPools),
+                                 PrevalenceSite = SiteTruePrev,
+                                 PrevalenceVillage = VillageTruePrev,
+                                 PrevalenceRegion = RegionPrevs[[R]]))
+      }
+      SizeSmallPool <- Catch %% MaxPoolSize
+      if(SizeSmallPool){
+        Data <- rbind(Data,
+                      data.frame(Region = R,
+                                 Village = paste(R,V,sep = "-"),
+                                 Site = paste(R,V,S,sep = "-"),
+                                 PoolSize = SizeSmallPool,
+                                 PrevalenceSite = SiteTruePrev,
+                                 PrevalenceVillage = VillageTruePrev,
+                                 PrevalenceRegion = RegionPrevs[[R]]))
+      }
+    }
+  }
+}
+Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < (1-(1-PrevalenceSite)^PoolSize)))
+
+# Calculating prevalences at different levels ignoring hierarchical sampling structure
+PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
+PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
+PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)
+
+# Calulcating prevalences at different levels acknowledging hierarchical structure
+
+# Similar to above but in a regresison framework with Region as population
+# effect (aka fixed effect) and Village and Site as group effects (aka random
+# effect)
+
+HierPrevModel <- PoolRegBayes(Data, Result ~ Region + (1|Village/Site), PoolSize)
+HierPrevs <- getPrevalence(HierPrevModel) # Gett fitted prevalence at each level: Population Effects only (in this case this is region), Population Effects and Village, and population effects, village and site.
+
+```
+
+```{r HierComparisonRegion, echo=FALSE}
+PlotDataRegion <- PrevRegion %>%
+  unique %>%
+  select(Region, PrevMLE, CILow, CIHigh) %>%
+  mutate(Method = 'Basic MLE') %>%
+  rename(Prev = PrevMLE) %>%
+  bind_rows(PrevRegion %>%
+              unique %>%
+              select(Region, PrevBayes, CrILow, CrIHigh) %>%
+              mutate(Method = 'Basic Bayes') %>%
+              rename(Prev = PrevBayes,
+                     CILow= CrILow,
+                     CIHigh = CrIHigh)) %>%
+  bind_rows(Data %>%
+              select(Region,PrevalenceRegion) %>%
+              unique %>%
+              mutate(Method = "True") %>%
+              rename(Prev = PrevalenceRegion)) %>%
+  bind_rows(HierPrevs$PopulationEffects %>%
+              mutate(Method = 'Heirarchical Bayes') %>%
+              rename(Prev = Estimate,
+                     CILow = CrILow,
+                     CIHigh = CrIHigh) %>%
+              select(Region, Prev, CILow, CIHigh, Method))
+
+PlotsRegion <- PlotDataRegion %>%
+  ggplot() +
+  geom_pointrange(aes(x = Method,
+                      color = Region,
+                      y = Prev,
+                      ymin = CILow,
+                      ymax = CIHigh,
+                      shape = Method)) +
+  facet_grid(~Region,scales = "free_x") +
+  #scale_y_continuous(labels=scales::percent) +
+  scale_y_log10(labels=scales::percent) +
+  scale_x_discrete(breaks = NULL)+
+  theme(axis.text.x = element_text(angle = 90)) +
+  ylab('Prevalence')
+PlotsRegion
+
+```
+```{r HierComparisonVillage, echo=FALSE}
+PlotDataVillage <- PrevVillage %>%
+  unique %>%
+  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
+  mutate(Method = 'Basic MLE') %>%
+  rename(Prev = PrevMLE) %>%
+  bind_rows(PrevVillage %>%
+              unique %>%
+              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
+              mutate(Method = 'Basic Bayes') %>%
+              rename(Prev = PrevBayes,
+                     CILow= CrILow,
+                     CIHigh = CrIHigh)) %>%
+  bind_rows(Data %>%
+              select(Region, Village,PrevalenceVillage) %>%
+              unique %>%
+              mutate(Method = "True") %>%
+              rename(Prev = PrevalenceVillage)) %>%
+  bind_rows(HierPrevs$Village %>%
+              mutate(Method = 'Heirarchical Bayes') %>%
+              rename(Prev = Estimate,
+                     CILow = CrILow,
+                     CIHigh = CrIHigh) %>%
+              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
+    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
+  subset(VillageNum %in% 1:5)
+
+PlotsVillage <- PlotDataVillage%>%
+  ggplot() +
+  geom_pointrange(aes(x = Village,
+                      color = Region,
+                      y = Prev,
+                      ymin = CILow,
+                      ymax = CIHigh,
+                      shape = Method),
+                  position = position_dodge(width = 0.8)) +
+  facet_grid(~Region,scales = "free_x") +
+  #scale_y_continuous(labels=scales::percent) +
+  scale_y_log10(labels=scales::percent) +
+  scale_x_discrete(breaks = NULL)+
+  theme(axis.text.x = element_text(angle = 90)) +
+  ylab('Prevalence')
+PlotsVillage
+
+```

### 2020-08-13 R/BayesPoolLogitReg.R

@@ -1,102 +1,0 @@
-#' Bayesian Logistic Regression with Presence/Absence Tests on Pooled Samples
-#'
-#' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool
-#'             and any number of columns to be used as the dependent variables in the
-#'             logistic regression
-#' @param PoolSize A \code{string} giving the name of the column with number of specimens/isolates/insects in each pool
-#' @param formula A \code{formula} of the kind used to define models in \code{glm}. The left-hand
-#'                side should be the name of column with the result of each test on each pooled
-#'                sample. The result must be stored with 1 indicating a positive test result and
-#'                0 indicating a negative test result.
-#' @param alpha The confidence level to be used for the confidence and credible intervals.
-#'              Defaults to 0.5\% (i.e. 95\% intervals)
-#' @param verbose Logical indicating whether to print progress to screen. Defaults to false
-#'                (no printing to screen)
-#' @return TBC
-#'
-#' @examples
-#' #Create a synthetic dataset of prevalence in different times and places
-#' #Locations A-C have different baseline prevalences.
-#' #Prevalence at D = Prevalence at A.
-#' #All locations have the same expoential growth rate, -0.5, i.e. falling prevalence
-#'
-#' N <- 500
-#' DataTrend <- data.frame(Place = sample(c("A","B","C","D"),N, replace = TRUE),
-#'                         Year = sample(c(0:2), N, replace = TRUE),
-#'                         NumInPool = sample(25:30, N, replace = TRUE)
-#'                         )
-#' BasePrev <- c(A = 0.1, B = 0.05, C = 0.02, D = 0.1) #The baseline prevalences at each location
-#' GrowthRate = -0.5 #The (negative) growth rate
-#' #Calculate the true prevalence at each time and place
-#' DataTrend$TruePrev <- with(DataTrend,
-#'                           BasePrev[Place] * exp(GrowthRate*(Year-min(Year))))
-#' #Simulate some pooled samples from each location
[…]

### 2020-08-13 R/HierPoolPrev.R

@@ -1,0 +1,132 @@
+#' Estimation of prevalence based on presence/absence tests on pooled samples in
+#' a heirarchical sampling frame
+#'
+#' @export
+#' @param data A \code{data.frame} with one row for each pooled sampled and
+#'   columns for the size of the pool (i.e. the number of specimens / isolates /
+#'   insects pooled to make that particular pool), the result of the test of the
+#'   pool. It may also contain additional columns with additional information
+#'   (e.g. location where pool was taken) which can optionally be used for
+#'   splitting the data into smaller groups and calculting prevalence by group
+#'   (e.g. calculating prevalence for each location)
+#' @param result The name of column with the result of each test on each pooled
+#'   sample. The result must be stored with 1 indicating a positive test result
+#'   and 0 indicating a negative test result.
+#' @param poolSize The name of the column with number of
+#'   specimens/isolates/insects in each pool
+#' @param hierarchy The name of column(s) indicating the group membership. In a
+#'   nested sampling design with multiple levels of grouping the lower-level
+#'   groups must have names/numbers that differentiate them from all other
+#'   groups at the same level. E.g. If sampling was performed at 200 sites
+#'   across 10 villages (20 site per village), then there should be 200 unique
+#'   names for the sites. If, for instance, the sites are instead numbered 1 to
+#'   20 within each village, the village identifier (e.g. A, B, C...) should be
+#'   combined with the site number to create unqiue identifiers for each site
+#'   (e.g. A-1, A-2... for sites in village A and B-1, B-2... for the sites in
+#'   village B etc.)
+#' @param ... Optional name(s) of columns with variables to group the data by.
+#'   If ommitted the complete dataset is used to estimate a single prevalence.
+#'   If included prevalence is estimated spearately for each group defined by
+#'   these columns
+#' @param prior.alpha,prior.beta,prior.absent The prior on the prevalence in
+#'   each group takes the form of beta distribution (with parameters alpha and
+#'   beta) modified to have a point mass of zero i.e. allowing for some prior
+#'   proability that the true prevalence is exactly zero (prior.absent) The
+#'   default is \code{prior.alpha = prior.beta = 1/2, prior.absent = 0} i.e. the
[…]

### 2020-08-13 R/PoolLogitReg.R

@@ -1,32 +1,0 @@
-#' Frequentist Logistic Regression with Presence/Absence Tests on Pooled Samples
-#'
-#' It can be useful to do logistic regression on the presence/absence results from
-#' pooled samples, however one must adjust for the size of each pool to correctly
-#' identify trends and associations. This can done using \code{glm} from the \code{stats}
-#'  package and the custom link function \code{\link{PoolLink}}, defined in this package.
-#'  \code{PoolLogitReg} is provided as a more convenient way to fit the same model
-#'
-#' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool
-#'             and any number of columns to be used as the dependent variables in the
-#'             logistic regression
-#' @param PoolSize The name of the column with number of specimens/isolates/insects in each pool
-#' @param formula A \code{formula} of the kind used to define models in \code{glm}. The left-hand
-#'                side should be the name of column with the result of each test on each pooled
-#'                sample. The result must be stored with 1 indicating a positive test result and
-#'                0 indicating a negative test result.
-#' @return An object of class \code{glm} with the regression outputs
-#'
-#' @example examples/LogisticRegression.R
-
-
-PoolLogitReg <- function (data, formula, PoolSize){
-  PoolSize <- enquo(PoolSize)
-  PoolSize <- select(data,!! PoolSize)[,1]
-   out <- glm(formula,
-              family = binomial(PoolLink(PoolSize)),
-              data = data)
-   return(out)
-}

### 2020-08-13 R/PoolLogitRegMixed.R

@@ -1,48 +1,0 @@
-#' Frequentist Mixed Effect Logistic Regression with Presence/Absence Tests on Pooled Samples
-#'
-#' It can be useful to do mixed effects logistic regression on the presence/absence results from
-#' pooled samples, however one must adjust for the size of each pool to correctly
-#' identify trends and associations. This can done using \code{glmer} from the \code{lme4}
-#' package and the custom link function \code{\link{PoolLink}}, defined in this package.
-#' \code{PoolLogitRegMixed} is provided as a more convenient way to fit the same model.
-#' \code{PoolLogitReg} is similar but for the case with only population/fixed effects.
-#' \code{PoolLogitRegMixed} should be used whenever there is some heirarchical structure
-#' to te sampling frame, or in other cases where a model with group/random effects is appropriate.
-#'
-#' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool
-#'             and any number of columns to be used as the dependent variables in the
-#'             logistic regression
-#' @param PoolSize The name of the column with number of specimens/isolates/insects in each pool
-#' @param formula A \code{formula} of the kind used to define models in \code{lme4}. The left-hand
-#'                side should be the name of column with the result of each test on each pooled
-#'                sample. The result must be stored with 1 indicating a positive test result and
-#'                0 indicating a negative test result.
-#' @return An object of class \code{glm} with the regression outputs
-#'
-#' @example examples/LogisticRegression.R!!!
-
-
-
-PoolLogitRegMixed <- function (data, formula, PoolSize){
-  PoolSize <- enquo(PoolSize)
-  PoolSize <- select(data,!! PoolSize)[,1]
-
-  # This method of determining whether a formula has any random/mixed effects
-  # is pretty much lifted straight from lme4
-  if(!length(findbars(formula[[length(formula)]]))){
-    warning("Model has no group/random effects. Using a generalised linear model instead")
-    out <- glm(formula,
-               family = binomial(PoolLink(PoolSize)),
-               data = data)
-  }else{
-    out <- glmer(formula,
-                 family = binomial(PoolLink(PoolSize)),
-                 data = data)
-  }
-
-  return(out)
-}
-

### 2020-08-13 R/PoolPrev.R

@@ -8,10 +8,10 @@
 #'             location where pool was taken) which can optionally be used for splitting
 #'             the data into smaller groups and calculting prevalence by group (e.g.
 #'             calculating prevalence for each location)
-#' @param TestResult The name of column with the result of each test on each pooled sample.
+#' @param result The name of column with the result of each test on each pooled sample.
 #'                   The result must be stored with 1 indicating a positive test result and
 #'                   0 indicating a negative test result.
-#' @param PoolSize The name of the column with number of specimens/isolates/insects in each pool
+#' @param poolSize The name of the column with number of specimens/isolates/insects in each pool
 #' @param ... Optional name(s) of columns with variables to group the data by.
 #'            If ommitted the complete dataset is used to estimate a single prevalence.
 #'            If included prevalence is estimated spearately for each group defined by these columns
@@ -38,11 +38,11 @@
 #' @example examples/Prevalence.R
 
 
-PoolPrev <- function(data,TestResult,PoolSize,...,
+PoolPrev <- function(data,result,poolSize,...,
                      prior.alpha = 0.5, prior.beta = 0.5, prior.absent = 0,
-                     alpha=0.05, verbose = F){
-  TestResult <- enquo(TestResult) #The name of column with the result of each test on each pooled sample
-  PoolSize <- enquo(PoolSize) #The name of the column with number of bugs in each pool
+                     alpha=0.05, verbose = F,cores = 1){
+  result <- enquo(result) #The name of column with the result of each test on each pooled sample
+  poolSize <- enquo(poolSize) #The name of the column with number of bugs in each pool
   group_var <- enquos(...) #optional name(s) of columns with other variable to group by. If ommitted uses the complete dataset of pooled sample results to calculate a single prevalence
 
   if(length(group_var) == 0){ #if there are no grouping variables
@@ -61,8 +61,8 @@ PoolPrev <- function(data,TestResult,PoolSize,...,
     #options(mc.cores = num_workers)
     sdata <- list(N = nrow(data),
                   #Result = array(data$Result), #PERHAPS TRY REMOVING COLUMN NAMES?
-                  Result = dplyr::select(data, !! TestResult)[,1] %>% as.matrix %>% as.numeric %>% array, #This seems a rather obscene way to select a column, but other more sensible methods have inexplicible errors when passed to rstan::sampling
-                  PoolSize = dplyr::select(data, !! PoolSize)[,1] %>% as.matrix %>% array,
[…]

### 2020-08-13 R/PoolReg.R

@@ -1,0 +1,71 @@
+#' Frequentist Mixed or Fixed Effect Logistic Regression with Presence/Absence Tests on
+#' Pooled Samples
+#'
+#' It can be useful to do mixed effects logistic regression on the
+#' presence/absence results from pooled samples, however one must adjust for the
+#' size of each pool to correctly identify trends and associations. This can
+#' done using \code{glmer} from the \code{lme4} package and the custom link
+#' function \code{\link{PoolLink}}, defined in this package.
+#' \code{PoolLogitRegMixed} is provided as a more convenient way to fit the same
+#' model. \code{PoolLogitReg} is similar but for the case with only
+#' population/fixed effects. \code{PoolLogitRegMixed} should be used whenever
+#' there is some heirarchical structure to te sampling frame, or in other cases
+#' where a model with group/random effects is appropriate.
+#'
+#' @export
+#' @param data A \code{data.frame} with one row for each pooled sampled and
+#'   columns for the size of the pool (i.e. the number of specimens / isolates /
+#'   insects pooled to make that particular pool), the result of the test of the
+#'   pool and any number of columns to be used as the dependent variables in the
+#'   logistic regression
+#' @param poolSize The name of the column with number of
+#'   specimens/isolates/insects in each pool
+#' @param formula A \code{formula} of the kind used to define models in
+#'   \code{lme4}, which are generalisation of the formulae used in \code{lm} or
+#'   \code{glm} that allow for random/group effects. The left-hand side of the
+#'   formula should be the name of column in \code{data} with the result of the
+#'   test on the pooled samples. The result must be stored with 1 indicating a
+#'   positive test result and 0 indicating a negative test result.
+#' @return An object of class \code{glmerMod} (or \code{glm} if there are no
+#'   random/group effects)
+#'
+#' @example examples/LogisticRegression.R!!!
+
+
+
+PoolReg <- function (data, formula, poolSize){
+  poolSize <- enquo(poolSize)
+
+  AllVars <- all.vars(formula)
+
+  if(!(as_label(poolSize) %in% colnames(data))){
+    stop("poolSize does not match any of the variable names in the the data provided.")
+  }
+  poolSize <- select(data,!! poolSize)[,1]
+
+  if(!all(AllVars %in% colnames(data))){
+    stop("formula contains variables that aren't in the data: ",
+         paste(AllVars[!(AllVars %in% colnames(data))], collapse = ", "))
+  }
[…]

### 2020-08-13 R/PoolRegBayes.R

@@ -1,46 +1,78 @@
-#' Bayesian Mixed (or fixed) Effect Logistic Regression with Presence/Absence Tests on Pooled Samples
+#' Bayesian Mixed or Fixed Effect Logistic Regression with Presence/Absence
+#' Tests on Pooled Samples
 #'
-#' It can be useful to do mixed effects logistic regression on the presence/absence results from
-#' pooled samples, however one must adjust for the size of each pool to correctly
-#' identify trends and associations.
+#' It can be useful to do mixed effects logistic regression on the
+#' presence/absence results from pooled samples, however one must adjust for the
+#' size of each pool to correctly identify trends and associations.
 #'
 #' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool
-#'             and any number of columns to be used as the dependent variables in the
-#'             logistic regression
-#' @param PoolSize The name of the column with number of specimens/isolates/insects in each pool
-#' @param formula A \code{formula} of the kind used to define models in \code{lme4} or \code{brms}.
-#'                The left-hand side should be the name of column with the result of each test on
-#'                each pooled sample. The result must be stored with 1 indicating a positive test
-#'                result and 0 indicating a negative test result.
-#' @return An object of class \code{brms} with the regression outputs
+#' @param data A \code{data.frame} with one row for each pooled sampled and
+#'   columns for the size of the pool (i.e. the number of specimens / isolates /
+#'   insects pooled to make that particular pool), the result of the test of the
+#'   pool and any number of columns to be used as the dependent variables in the
+#'   logistic regression.
+#' @param poolSize The name of the column with number of specimens / isolates /
+#'   insects in each pool.
+#' @param formula A \code{formula} of the kind used to define models in
+#'   \code{brms}, which are generalisation of the formulae used in \code{lm,glm}
+#'   or \code{lme4}. The left-hand side of the formula should be the name of
+#'   column in \code{data} with the result of the test on the pooled samples.
[…]

### 2020-08-13 R/PoolTestR-package.R

@@ -18,10 +18,12 @@
 #' @import Rcpp
 #' @import rstan
 #' @import lme4
+#' @import brms
 #' @importFrom stats qchisq uniroot quantile model.matrix quantile na.omit terms reformulate
 #' @importFrom parallel detectCores
 #' @importFrom tidyr unite
 #' @importFrom vcd structable
+#' @importFrom stringr str_match_all
 #'
 #' @references
 #' Stan Development Team (2019). RStan: the R interface to Stan. R package version 2.19.2. https://mc-stan.org

### 2020-08-13 R/PooledLogitRegressionBinom.R

@@ -1,79 +1,0 @@
-#' Logistic regression with presence/absence tests on pooled samples
-#'
-#' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool
-#'             and any number of columns to be used as the dependent variables in the
-#'             logistic regression
-#' @param PoolSize A \code{string} giving the name of the column with number of specimens/isolates/insects in each pool
-#' @param formula A \code{formula} of the kind used to define models in \code{glm}. The left-hand
-#'                side should be the name of column with the result of each test on each pooled
-#'                sample. The result must be stored with 1 indicating a positive test result and
-#'                0 indicating a negative test result.
-#' @param alpha The confidence level to be used for the confidence and credible intervals.
-#'              Defaults to 0.5\% (i.e. 95\% intervals)
-#' @param verbose Logical indicating whether to print progress to screen. Defaults to false
-#'                (no printing to screen)
-#' @return TBC
-#'
-
-PooledRegressionBinom <- function(data, PoolSize, formula, alpha=0.05,verbose = F){
-
-  if(!attr(terms(formula),"response")){
-    stop("formula needs left hand side")
-  }
-  Result <- all.vars(formula)[1]
-
-  #Make a count of the number of cases in each time period and each group (defined by covariates supplied on the rhs of Formula)
-
-  GroupingVars <- labels(terms(formula))
-  print(GroupingVars)
-  if(length(GroupingVars) == 0){
-    stop("formula needs a right-hand side")
-  }
-
-  #Drop irrelevant columns and rows with missing values
-  data <- data[,c(PoolSize,GroupingVars,Result),drop = F] %>% na.omit
-
-
-  dataCount <- table(data[,c(PoolSize,GroupingVars,Result)]) %>%
-    as.data.frame() %>%
-    unite(Group,GroupingVars,sep=".") %>%
-    structable(data = ., reformulate(c(PoolSize,Result,"Group"))) %>%
-    as.table
-
-  #Get the model matrix
-  ReducedModelMatrix<- function(formula, data){
-    ResVarsNames <- labels(terms(formula))
-    Counts = data %>%
-      select_at(ResVarsNames) %>%
-      group_by_at(ResVarsNames) %>%
-      count()
[…]

### 2020-08-13 R/getPrevalence.R

@@ -1,0 +1,84 @@
+#' Predicting Prevalence from a Bayesian Mixed or Fixed Effect Logistic
+#' Regression with Presence/Absence Tests on Pooled Samples
+#'
+#' This function works somewhat like a \code{predict} or \code{fitted} generic
+#' function returning the model predicted prevalence for a given set of data;
+#' however, as the quantity of interest (prevalence) is neither on the response
+#' or link scale we do not use either of these generic functions. Further, when
+#' the model accounts for the heirarchical structure of the sampling frame (e.g.
+#' Region/Village/Site), it is typical to want to know the predicted values at
+#' each level of sampling (e.g. Prevalence at each region, village or site) so
+#' these are calculated automatically.
+#'
+#' @export
+#' @param model An object of class \code{brms} with the regression outputs from
+#'   a call to \code{PoolRegBayes}
+#' @param data The data for which prevalence needs to be estimated/predicted. If
+#'   not provided, defaults to using the data used to train the model (i.e.
+#'   returns the fitted values of the prevalence)
+#' @return A \code{list} with at least one field \code{PopulationEffects} and an
+#'   additional field for every random/group effect variable. The field
+#'   \code{PopulationEffects} contains a \code{data.frame} with the prevalence
+#'   estimated based only the fixed/population effects. When the intercept is
+#'   the only fixed/popultion effect, this is just the population mean (possibly
+#'   adjusted for random/group effects). When there are also
+#'
+#' @example examples/LogisticRegression.R!!!
+
+getPrevalence <- function(model,data = model$data){
+  formula <- model$formula$pforms$eta
+  PoolSizeName <- sub(".*\\^", "",as.character(model$formula$formula)[[3]]) #The name of the pool size variable in data
+  GroupTermNames <- (as.character(formula)[[3]] %>%
+                       str_match_all("\\|\\s*(.*?)\\s*\\)"))[[1]][,2] %>%
+    strsplit(split = "\\/") %>%
+    unlist
+  NGroupTerms <- length(GroupTermNames)
+
+  AllTerms <- intersect(colnames(data),unique(c(GroupTermNames, attr(terms(formula),"term.labels"))))
+  PopTerms <- setdiff(AllTerms,GroupTermNames)
+
+  #Datapoints to make prediction at
[…]

### 2020-08-13 R/stanmodels.R

@@ -1,12 +1,11 @@
 # Generated by rstantools.  Do not edit by hand.
 
 # names of stan models
-stanmodels <- c("BayesianPoolScreen", "PooledLogisticRegression", "PooledLogisticRegressionBinom")
+stanmodels <- c("BayesianPoolScreen", "HierBayesianPoolScreen")
 
 # load each stan module
 Rcpp::loadModule("stan_fit4BayesianPoolScreen_mod", what = TRUE)
-Rcpp::loadModule("stan_fit4PooledLogisticRegression_mod", what = TRUE)
-Rcpp::loadModule("stan_fit4PooledLogisticRegressionBinom_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4HierBayesianPoolScreen_mod", what = TRUE)
 
 # instantiate each stanmodel object
 stanmodels <- sapply(stanmodels, function(model_name) {

### 2020-08-13 src/RcppExports.cpp

@@ -8,13 +8,11 @@ using namespace Rcpp;
 
 
 RcppExport SEXP _rcpp_module_boot_stan_fit4BayesianPoolScreen_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4PooledLogisticRegression_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4PooledLogisticRegressionBinom_mod();
+RcppExport SEXP _rcpp_module_boot_stan_fit4HierBayesianPoolScreen_mod();
 
 static const R_CallMethodDef CallEntries[] = {
     {"_rcpp_module_boot_stan_fit4BayesianPoolScreen_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4BayesianPoolScreen_mod, 0},
-    {"_rcpp_module_boot_stan_fit4PooledLogisticRegression_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4PooledLogisticRegression_mod, 0},
-    {"_rcpp_module_boot_stan_fit4PooledLogisticRegressionBinom_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4PooledLogisticRegressionBinom_mod, 0},
+    {"_rcpp_module_boot_stan_fit4HierBayesianPoolScreen_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4HierBayesianPoolScreen_mod, 0},
     {NULL, NULL, 0}
 };
 

### 2020-08-13 src/stanExports_HierBayesianPoolScreen.cc

@@ -1,0 +1,32 @@
+// Generated by rstantools.  Do not edit by hand.
+
+#include <Rcpp.h>
+using namespace Rcpp ;
+#include "stanExports_HierBayesianPoolScreen.h"
+
+RCPP_MODULE(stan_fit4HierBayesianPoolScreen_mod) {
+
+
+    class_<rstan::stan_fit<stan_model, boost::random::ecuyer1988> >("model_HierBayesianPoolScreen")
+
+    .constructor<SEXP,SEXP,SEXP>()
+
+
+    .method("call_sampler", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::call_sampler)
+    .method("param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names)
+    .method("param_names_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names_oi)
+    .method("param_fnames_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_fnames_oi)
+    .method("param_dims", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims)
+    .method("param_dims_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims_oi)
+    .method("update_param_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::update_param_oi)
+    .method("param_oi_tidx", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_oi_tidx)
+    .method("grad_log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::grad_log_prob)
+    .method("log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::log_prob)
+    .method("unconstrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrain_pars)
+    .method("constrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::constrain_pars)
+    .method("num_pars_unconstrained", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::num_pars_unconstrained)
+    .method("unconstrained_param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrained_param_names)
[…]

### 2020-08-13 src/stanExports_HierBayesianPoolScreen.h

@@ -1,0 +1,504 @@
+// Generated by rstantools.  Do not edit by hand.
+
+/*
+    PoolTestR is free software: you can redistribute it and/or modify
+    it under the terms of the GNU General Public License as published by
+    the Free Software Foundation, either version 3 of the License, or
+    (at your option) any later version.
+
+    PoolTestR is distributed in the hope that it will be useful,
+    but WITHOUT ANY WARRANTY; without even the implied warranty of
+    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+    GNU General Public License for more details.
+
+    You should have received a copy of the GNU General Public License
+    along with PoolTestR.  If not, see <http://www.gnu.org/licenses/>.
+*/
+#ifndef MODELS_HPP
+#define MODELS_HPP
+#define STAN__SERVICES__COMMAND_HPP
+#include <rstan/rstaninc.hpp>
+// Code generated by Stan version 2.19.1
+#include <stan/model/model_header.hpp>
+namespace model_HierBayesianPoolScreen_namespace {
+using std::istream;
+using std::string;
+using std::stringstream;
+using std::vector;
+using stan::io::dump;
+using stan::math::lgamma;
+using stan::model::prob_grad;
+using namespace stan::math;
+static int current_statement_begin__;
+stan::io::program_reader prog_reader__() {
+    stan::io::program_reader reader;
+    reader.add_event(0, 0, "start", "model_HierBayesianPoolScreen");
+    reader.add_event(48, 46, "end", "model_HierBayesianPoolScreen");
+    return reader;
+}
+#include <stan_meta_header.hpp>
+class model_HierBayesianPoolScreen : public prob_grad {
+private:
+        int N;
+        int L;
+        std::vector<int> NumGroups;
+        int TotalGroups;
+        std::vector<int> Result;
+        vector_d PoolSize;
+        matrix_d Z;
+        double PriorAlpha;
+        double PriorBeta;
+        vector_d Zw;
+        std::vector<int> Zv;
+        std::vector<int> Zu;
+public:
+    model_HierBayesianPoolScreen(stan::io::var_context& context__,
+        std::ostream* pstream__ = 0)
+        : prob_grad(0) {
+        ctor_body(context__, 0, pstream__);
+    }
+    model_HierBayesianPoolScreen(stan::io::var_context& context__,
+        unsigned int random_seed__,
+        std::ostream* pstream__ = 0)
[…]

### 2020-08-13 src/stanExports_PooledLogisticRegression.cc

@@ -1,32 +1,0 @@
-// Generated by rstantools.  Do not edit by hand.
-
-#include <Rcpp.h>
-using namespace Rcpp ;
-#include "stanExports_PooledLogisticRegression.h"
-
-RCPP_MODULE(stan_fit4PooledLogisticRegression_mod) {
-
-
-    class_<rstan::stan_fit<stan_model, boost::random::ecuyer1988> >("model_PooledLogisticRegression")
-
-    .constructor<SEXP,SEXP,SEXP>()
-
-
-    .method("call_sampler", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::call_sampler)
-    .method("param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names)
-    .method("param_names_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names_oi)
-    .method("param_fnames_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_fnames_oi)
-    .method("param_dims", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims)
-    .method("param_dims_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims_oi)
-    .method("update_param_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::update_param_oi)
-    .method("param_oi_tidx", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_oi_tidx)
-    .method("grad_log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::grad_log_prob)
-    .method("log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::log_prob)
-    .method("unconstrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrain_pars)
-    .method("constrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::constrain_pars)
-    .method("num_pars_unconstrained", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::num_pars_unconstrained)
-    .method("unconstrained_param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrained_param_names)
[…]

### 2020-08-13 src/stanExports_PooledLogisticRegression.h

@@ -1,529 +1,0 @@
-// Generated by rstantools.  Do not edit by hand.
-
-/*
-    PoolTestR is free software: you can redistribute it and/or modify
-    it under the terms of the GNU General Public License as published by
-    the Free Software Foundation, either version 3 of the License, or
-    (at your option) any later version.
-
-    PoolTestR is distributed in the hope that it will be useful,
-    but WITHOUT ANY WARRANTY; without even the implied warranty of
-    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-    GNU General Public License for more details.
-
-    You should have received a copy of the GNU General Public License
-    along with PoolTestR.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#ifndef MODELS_HPP
-#define MODELS_HPP
-#define STAN__SERVICES__COMMAND_HPP
-#include <rstan/rstaninc.hpp>
-// Code generated by Stan version 2.19.1
-#include <stan/model/model_header.hpp>
-namespace model_PooledLogisticRegression_namespace {
-using std::istream;
-using std::string;
-using std::stringstream;
-using std::vector;
-using stan::io::dump;
-using stan::math::lgamma;
-using stan::model::prob_grad;
-using namespace stan::math;
-static int current_statement_begin__;
-stan::io::program_reader prog_reader__() {
-    stan::io::program_reader reader;
-    reader.add_event(0, 0, "start", "model_PooledLogisticRegression");
-    reader.add_event(42, 40, "end", "model_PooledLogisticRegression");
-    return reader;
-}
-#include <stan_meta_header.hpp>
-class model_PooledLogisticRegression : public prob_grad {
-private:
-        int N;
-        int A;
-        std::vector<int> Result;
-        std::vector<int> PoolSize;
-        matrix_d MM;
-        matrix_d RegMM;
-        vector_d R;
-        row_vector_d r;
-public:
-    model_PooledLogisticRegression(stan::io::var_context& context__,
-        std::ostream* pstream__ = 0)
-        : prob_grad(0) {
-        ctor_body(context__, 0, pstream__);
-    }
-    model_PooledLogisticRegression(stan::io::var_context& context__,
-        unsigned int random_seed__,
-        std::ostream* pstream__ = 0)
-        : prob_grad(0) {
-        ctor_body(context__, random_seed__, pstream__);
-    }
-    void ctor_body(stan::io::var_context& context__,
-                   unsigned int random_seed__,
-                   std::ostream* pstream__) {
[…]

### 2020-08-13 src/stanExports_PooledLogisticRegressionBinom.cc

@@ -1,32 +1,0 @@
-// Generated by rstantools.  Do not edit by hand.
-
-#include <Rcpp.h>
-using namespace Rcpp ;
-#include "stanExports_PooledLogisticRegressionBinom.h"
-
-RCPP_MODULE(stan_fit4PooledLogisticRegressionBinom_mod) {
-
-
-    class_<rstan::stan_fit<stan_model, boost::random::ecuyer1988> >("model_PooledLogisticRegressionBinom")
-
-    .constructor<SEXP,SEXP,SEXP>()
-
-
-    .method("call_sampler", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::call_sampler)
-    .method("param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names)
-    .method("param_names_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_names_oi)
-    .method("param_fnames_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_fnames_oi)
-    .method("param_dims", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims)
-    .method("param_dims_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_dims_oi)
-    .method("update_param_oi", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::update_param_oi)
-    .method("param_oi_tidx", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::param_oi_tidx)
-    .method("grad_log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::grad_log_prob)
-    .method("log_prob", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::log_prob)
-    .method("unconstrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrain_pars)
-    .method("constrain_pars", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::constrain_pars)
-    .method("num_pars_unconstrained", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::num_pars_unconstrained)
-    .method("unconstrained_param_names", &rstan::stan_fit<stan_model, boost::random::ecuyer1988> ::unconstrained_param_names)
[…]

### 2020-08-13 src/stanExports_PooledLogisticRegressionBinom.h

@@ -1,534 +1,0 @@
-// Generated by rstantools.  Do not edit by hand.
-
-/*
-    PoolTestR is free software: you can redistribute it and/or modify
-    it under the terms of the GNU General Public License as published by
-    the Free Software Foundation, either version 3 of the License, or
-    (at your option) any later version.
-
-    PoolTestR is distributed in the hope that it will be useful,
-    but WITHOUT ANY WARRANTY; without even the implied warranty of
-    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-    GNU General Public License for more details.
-
-    You should have received a copy of the GNU General Public License
-    along with PoolTestR.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#ifndef MODELS_HPP
-#define MODELS_HPP
-#define STAN__SERVICES__COMMAND_HPP
-#include <rstan/rstaninc.hpp>
-// Code generated by Stan version 2.19.1
-#include <stan/model/model_header.hpp>
-namespace model_PooledLogisticRegressionBinom_namespace {
-using std::istream;
-using std::string;
-using std::stringstream;
-using std::vector;
-using stan::io::dump;
-using stan::math::lgamma;
-using stan::model::prob_grad;
-using namespace stan::math;
-static int current_statement_begin__;
-stan::io::program_reader prog_reader__() {
-    stan::io::program_reader reader;
-    reader.add_event(0, 0, "start", "model_PooledLogisticRegressionBinom");
-    reader.add_event(37, 35, "end", "model_PooledLogisticRegressionBinom");
-    return reader;
-}
-#include <stan_meta_header.hpp>
-class model_PooledLogisticRegressionBinom : public prob_grad {
-private:
-        int N;
-        std::vector<int> PoolSizes;
-        int G;
-        std::vector<std::vector<int> > PosPools;
-        std::vector<std::vector<int> > NegPools;
-        int A;
-        matrix_d MM;
-        std::vector<std::vector<int> > TotPools;
-public:
-    model_PooledLogisticRegressionBinom(stan::io::var_context& context__,
-        std::ostream* pstream__ = 0)
-        : prob_grad(0) {
-        ctor_body(context__, 0, pstream__);
-    }
-    model_PooledLogisticRegressionBinom(stan::io::var_context& context__,
-        unsigned int random_seed__,
-        std::ostream* pstream__ = 0)
-        : prob_grad(0) {
-        ctor_body(context__, random_seed__, pstream__);
-    }
[…]

### 2020-08-13 test/BayesPoolLogitReg.R

@@ -1,0 +1,102 @@
+#' Bayesian Logistic Regression with Presence/Absence Tests on Pooled Samples
+#'
+#' @export
+#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
+#'             the size of the pool (i.e. the number of specimens / isolates / insects
+#'             pooled to make that particular pool), the result of the test of the pool
+#'             and any number of columns to be used as the dependent variables in the
+#'             logistic regression
+#' @param PoolSize A \code{string} giving the name of the column with number of specimens/isolates/insects in each pool
+#' @param formula A \code{formula} of the kind used to define models in \code{glm}. The left-hand
+#'                side should be the name of column with the result of each test on each pooled
+#'                sample. The result must be stored with 1 indicating a positive test result and
+#'                0 indicating a negative test result.
+#' @param alpha The confidence level to be used for the confidence and credible intervals.
+#'              Defaults to 0.5\% (i.e. 95\% intervals)
+#' @param verbose Logical indicating whether to print progress to screen. Defaults to false
+#'                (no printing to screen)
+#' @return TBC
+#'
+#' @examples
+#' #Create a synthetic dataset of prevalence in different times and places
+#' #Locations A-C have different baseline prevalences.
+#' #Prevalence at D = Prevalence at A.
+#' #All locations have the same expoential growth rate, -0.5, i.e. falling prevalence
+#'
+#' N <- 500
+#' DataTrend <- data.frame(Place = sample(c("A","B","C","D"),N, replace = TRUE),
+#'                         Year = sample(c(0:2), N, replace = TRUE),
+#'                         NumInPool = sample(25:30, N, replace = TRUE)
+#'                         )
+#' BasePrev <- c(A = 0.1, B = 0.05, C = 0.02, D = 0.1) #The baseline prevalences at each location
+#' GrowthRate = -0.5 #The (negative) growth rate
+#' #Calculate the true prevalence at each time and place
+#' DataTrend$TruePrev <- with(DataTrend,
+#'                           BasePrev[Place] * exp(GrowthRate*(Year-min(Year))))
+#' #Simulate some pooled samples from each location
[…]

### 2020-08-13 test/HeirarchicalExamples.R

@@ -1,258 +1,0 @@
-#Heirarchical nested example where you should really be using a glmm
-
-pkgbuild::compile_dll()
-roxygen2::roxygenize()
-
-RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
-NumRegions <- length(RegionPrevs)
-NumVillages <- 10 #Villages per Region
-NumSites <- 15 #Sites per village
-MeanCatch <- 100; SDCatch <- 30 #Mean and SD of mosquito catch sizes
-DispersionCatch <- 1.5
-MaxPoolSize <- 25
-
-Data <- data.frame()
-TruePrev <- data.frame()
-for(R in names(RegionPrevs)){
-  for(V in 1:NumVillages){
-
-    VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + rnorm(1,mean = 0, sd = 0.5))
-
-    for(S in 1:NumSites){
-
-      SiteTruePrev <- plogis(qlogis(VillageTruePrev) + rnorm(1,mean = 0, sd = 0.25))
-
-
-      TruePrev <- rbind(TruePrev,
-                        data.frame(Region = R,
-                                   Village = paste(R,V,sep = "-"),
-                                   Site = paste(R,V,S,sep = "-"),
-                                   PrevalenceRegion = RegionPrevs[[R]],
-                                   PrevalenceVillage = VillageTruePrev,
-                                   PrevalenceSite = SiteTruePrev))
-
-      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes <= 0 to guarantee at least one mossie
-      CatchSizeMult <- SiteTruePrev/RegionPrevs[[R]]
-      Catch <- 0
-      while(Catch<=0){
-        Catch <- rnbinom(1,mu = MeanCatch * CatchSizeMult,DispersionCatch)
-      }
-      NumBigPools <- Catch %/% MaxPoolSize
-      if(NumBigPools){
-        Data <- rbind(Data,
-                      data.frame(Region = R,
-                                 Village = paste(R,V,sep = "-"),
-                                 Site = paste(R,V,S,sep = "-"),
-                                 PoolSize = rep(MaxPoolSize,NumBigPools),
-                                 PrevalenceSite = SiteTruePrev,
-                                 PrevalenceVillage = VillageTruePrev,
[…]

### 2020-08-13 test/HierarchicalExamples.R

@@ -1,0 +1,548 @@
+#Hierarchical nested example where you should really be using a glmm
+
+pkgbuild::compile_dll(force = T)
+pkgbuild::compile_dll()
+roxygen2::roxygenize()
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(plotly)
+
+RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
+SpeciesCatchSizeExp <- c(X = 0.5, Y = 0, Z = -0.5) # Are mosquito catch sizes for a species correlated with prevalence
+NumRegions <- length(RegionPrevs)
+NumVillages <- 10 #Villages per Region
+NumSites <- 15 #Sites per village
+MeanCatch <- 1000; #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
+DispersionCatch <- 5
+MaxPoolSize <- 25
+VillageSD <- 0.25
+SiteSD <- 0.1
+N <- 10^4
+
+#Plot catch size distribution
+plot(function(x){dnbinom(x,mu = MeanCatch, size = DispersionCatch)},from = 0, to =2000)
+
+Data <- data.frame()
+TruePrev <- data.frame()
+for(Sp in names(SpeciesCatchSizeExp)){
+  for(R in names(RegionPrevs)){
+    #Hypothetical true prevalence of region that we would measure by averaging the prevalence across a large number of sites and villages weighting for mosquito abundance
+    temp <- rnorm(N,mean = 0, sd = sqrt(SiteSD^2 + VillageSD^2)) #Generate lots of deviates for hypothetical sites
+    RegionTruePrevWeightedMeanLogit <- weighted.mean(plogis(qlogis(RegionPrevs[[R]]) + temp), exp(temp)^SpeciesCatchSizeExp[Sp])
+    RegionTruePrevLogitWeightedMean <- plogis(weighted.mean(qlogis(RegionPrevs[[R]]) + temp, exp(temp)^SpeciesCatchSizeExp[Sp]))
+    RegionTruePrevMeanLogit <- mean(plogis(qlogis(RegionPrevs[[R]]) + temp))
+    RegionTruePrevLogitMean <- RegionPrevs[[R]] # equal to plogis(mean(qlogis(RegionPrevs[[R]]) + temp))
+
+
+    for(V in 1:NumVillages){
+      #Difference of village prevalence from the region prevalence on log-odds scale
+      VillageDeviate <- rnorm(1,mean = 0, sd = VillageSD)
[…]

### 2020-09-17 paper/Paper.Rmd
reordered arguments in Regression functions to match R standards
Also allowed users to specify custom priors with PoolRegBayes

@@
 output:
+  word_document: default
   pdf_document: default
-  word_document: default
   html_document: default
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(cache.extra = R.version.string)
+knitr::opts_chunk$set(cache.extra = R.version)
+library(PoolTestR)
 ```
 
-[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen]
+[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen.[^2] ]
 
-We wish to estimate the prevalence, p, of a disease or molecular marker in a population from the results of tests on a pooled samples.
-For a pool combining N samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$.
+[^2]: We need to also talk about the existing R packages BinGroup and BinGroup2. Perhaps we can sell ourselves as offerring a more user-friendly approach?
+Can we make a shiny app which uses our package as the backend where people can upload their data?
+Also, we introduce heirarchical models (which they don't?)
+Also, we include by default Bayesian version (which they don't?)
+Also, we can calculate confidence intervals for any number of group sizes (which they can but only very slowly?)
+This website has a lot of work on group testing (he seems to have built his career around group-testing!) http://www.chrisbilder.com/grouptesting/
+
+We wish to estimate the prevalence, $p$, of a disease or molecular marker in a population from the results of tests on a pooled samples.
+For a pool combining $N$ samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$.
 If $M$ such pools from a single location are tested and $m$ of these are positive the maximum likelihood estimate (MLE) of $q\ is \frac{m}{M}$ and the MLE of the prevalence, $p$, in the population is ${1-\left(1-\frac{m}{M}\right)}^\frac{1}{N}$.
@@
 `PoolRegBayes` builds on the flexible non-linear modelling framework provided by the `brms` package to fit bayesian fixed and mixed effect regression models on data from pooled tests.
-By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of R.
+By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of `R`.
 
@@
 
-The boxes below demonstrated the use of `PoolPrev` on a synthetic dataset.
+The boxes below demonstrate the use of `PoolPrev` on a synthetic dataset.
 The synthetic dataset consists of 1000 pools from four different locations (A-D) over five years (0-4) of sampling.
@@
 
-```{r GenerateDataset, include=FALSE}
+```{r GenerateDataset, include=FALSE, cache=TRUE}
 library(dplyr)
@@
 
-```{r PoolPrevExample}
+```{r PoolPrevExample, warning=FALSE, cache=TRUE}
 #Looking at the first few rows of the synthetic dataset to see structure
@@
 
-### PoolLogitReg
-Given a dataset containing the number of samples, the result of tests for each pool, potential dependent variables associated with each pool, and a formula defining the model, `PoolLogitReg` fits a logistic regression model that adjusts for the sizes of pools.
-The output is a S3-object of class `glm` which supports that same methods (e.g.
-summary, predict, plot, confint) as any other object returned by the `glm` function.
+### Regression
+Our package provides tools for mixed-effect regression models in both a frequentist and Bayesian framework.
+`PoolReg` fits a frequentist mixed- or fixed-effect logistic regression model that adjusts for the sizes of pools.
+For a model with only fixed effects the output is a S3-object of class `glm`, while the output for a model with random effects is a S3-object of class 'glmerMod' which supports that same methods (e.g.
+summary, predict, plot, confint) as any other object returned by the `glm` or `glmer` functions.
+`PoolRegBayes` provides functionality to perform the same analyses in a Bayesian framework.
 
-The boxes below apply `PoolLogitReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.
+The boxes below apply `PoolReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.
 
-```{r PoolLogitRegExample}
+```{r PoolLogitRegExample, warning=FALSE, cache=TRUE}
 # Fit modified logistic regression model
 #The below two lines produce identical results and support all the same methods
-Reg <- PoolReg(Data,Result ~ Place + Year,
-                    NumInPool)
+Reg <- PoolReg(Result ~ Place + Year, Data, NumInPool)
 Reg.glm <- glm(Result ~ Place + Year,
@@
 Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
-```{r Comparison, echo=FALSE}
+```{r Comparison, echo=FALSE, warning=FALSE}
 library(ggplot2)
@@
 
-## Testing
-A more realistic example:
-- 3 regions with prevalence:
-  - low (0.5%)
-  - medium (2%)
-  - high (4%) 
-- 10 villages in each region with prevalence:
-  - random normal distribted tight around region average, or 
-  - one hotspot and one coldspot village
-- 15 sites at each village.
-  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
-  - Mosquitos pooled into test-tubes of 25 + one pool with remainder
+## Hierarchical Sampling Structure
+Many xenomonitoring surveys involve a hierarchical sampling structure.
+For instance if one wishes to understand the prevalence in a particular village, one may place traps at a number of sites around the village.
+The vectors caught at each site can then be tested individually or in pools.
+However, as prevalence may vary from site to site, the result of tests on individuals vectors or pools from the same site cannot be considered independent.
+However, the function `PoolPrev` in our package and other software like PoolScreen assume that results of pools are independent.
+Estimating the prevalence for the whole village ignoring this dependance will result in over-confident (narrow) estiamtion intervals.
+To account for this dependance we can use a hierarchical model.
+[^3]
 
-```{r GenerateMoreRealisticDataset}
+[^3]: Should we make some note about an alternate appraoch?
+i.e.
+If prevalence is not expected to vary much between sites and the number of vectors caught at each site are similar, one can combine the vectors trapped across the whole village and create pools from this common set of specimens.
+However, this may mask any variation between sites, discarding potentially useful spatial information.
+Our package provides two ways of accounting for hierarchy in the sampling frame.
+
+`HeirPoolPrev` fits an intercept-only hierarchical model.
+The syntax and outputs are very similar to `PoolPrev`.
+There is only one additional argument, `hierarchy`, describing the hierachical structure of the sampling frame.
+The output provides the Bayesian posterior mean and credible intervals for the prevalence, but unlike `PoolPrev` does not provide the maximum-likelihood estimate or likelihood ratio confidence intervals [^4].
+As with `PoolPrev` users can specify variables that split the dataset into subgroups.
+If subgroups of the data are specified, estimation proceeds independantly for each subgroup.
+
+A more flexible modelling approach is provided by the regression functions `PoolReg` and `PoolRegBayes` which can account for hierarchical sampling structure as random-effects or group-effects.
+The function `getPrevalence` provides a convenient way of extracting predicted prevalences and confidence intervals at each level of the sampling frame.
+
+We illustrate both approaches with another synthetic dataset with a realistic hierarchical sampling frame.
+We simulate samples taken from across three regions (A, B, and C) in which the vectors have a low (0.5\%), medium (2\%), and high (4\%) prevalence of the marker of interest.
+Within each region we choose ten villages, and within each of these villages we choose fifteen sites to place traps.
+Within each region prevalence varies between villages around the mean for the region, and within each village prevalence varies between sites around the mean for the village.
+A zero-truncated negative binomial number (mean 200, dispersion 5) of vectors are caught at each site.
+The catch size at each site is independent.
+The catches at each site are pooled into groups of 25 with an additional pool for any remainder (e.g.
+a catch of 53 vectors will be pooled into two pools of 25 and one pool of three).
+The test is assumed to have perfect sensitivity and specificity.
+
+[^4]: We could provide frequentist outputs too (MLE estimate and confidence intervals), but the confidence intervals get pretty tricky so I'd use bootstrapping which is just as slow as Bayesian analysis.
+I'm not sure there's much utility to this.
+`PoolPrev` has the frequentist options because that's what people who've used PoolScreen might expect (and it's easy).
+However, `HierPoolPrev` already departs from PoolScreen so people shouldn't have the same expectations.
+Besides, frequentist methods might be unstable or non-sensicle when all the pools from one of the sites are positive or negative
+
+```{r GenerateMoreRealisticDataset, include=FALSE, cache=TRUE}
 RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
@@
 Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < (1-(1-PrevalenceSite)^PoolSize)))
+```
+```{r HierarchicalPrevalence, warning=FALSE, cache=TRUE}
+# Calculating prevalences for each region ignoring hierarchical sampling frame
+PrevRegion <- PoolPrev(Data, Result, PoolSize, Region)
+# Calculating prevalences for each region acknowledging the hierarchical sampling frame
+PrevRegionHier <- HierPoolPrev(Data, Result, PoolSize, c('Site','Village'), Region)
 
-# Calculating prevalences at different levels ignoring hierarchical sampling structure
-PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
-PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
-PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)
+# Similar to above but in a more flexible mixed-effect regresison framework.
+# Here we treat region as a population effect (aka fixed effect) and Village and
+# Site as group effects (aka random effects). If we had additional covariates
+# (e.g. socio-geographic characteristics of each site or villages) we could also
+# include these as population effects
 
-# Calulcating prevalences at different levels acknowledging hierarchical structure
+# Fit a Bayesian model
+HierPrevModel <- PoolRegBayes(Result ~ Region + (1|Village/Site), Data, PoolSize)
+# Extracting  prevalence at each level from the fitted model. The output is a list with three entries:
+#     Prevalence for each combination of population effects (in this case this is region)
+#     Prevalence for each Village within each region
+#     Prevalence for each site within each village and region
+HierPrevs <- getPrevalence(HierPrevModel) 
+head(HierPrevs)
 
-# Similar to above but in a regresison framework with Region as population
-# effect (aka fixed effect) and Village and Site as group effects (aka random
-# effect)
-
-HierPrevModel <- PoolRegBayes(Data, Result ~ Region + (1|Village/Site), PoolSize)
-HierPrevs <- getPrevalence(HierPrevModel) # Gett fitted prevalence at each level: Population Effects only (in this case this is region), Population Effects and Village, and population effects, village and site.
-
+# Should we do the same thing but in a frequentist framework?
+We could get confidence intervals using bootMer?
+This is slower even than Bayesian inference, so I would always use (and suggest people use) the Bayesian version anyway.
+I have not implemented getPrevalence for the frequentist model yet, but it shouldn't be too hard if want to provide it as an option
+HierPrevModelFreq <- PoolReg(Result ~ Region + (1|Village/Site), Data, PoolSize)
 ```
 
-```{r HierComparisonRegion, echo=FALSE}
+```{r HierComparisonRegion, echo=FALSE,warning = FALSE}
 PlotDataRegion <- PrevRegion %>%
@@
 ```
-```{r HierComparisonVillage, echo=FALSE}
+```{r HierComparisonVillage, echo=FALSE, warning = FALSE}
 PlotDataVillage <- PrevVillage %>%

### 2020-09-17 R/HierPoolPrev.R

@@ -30,11 +30,11 @@
 #'   these columns
 #' @param prior.alpha,prior.beta,prior.absent The prior on the prevalence in
 #'   each group takes the form of beta distribution (with parameters alpha and
-#'   beta) modified to have a point mass of zero i.e. allowing for some prior
-#'   proability that the true prevalence is exactly zero (prior.absent) The
-#'   default is \code{prior.alpha = prior.beta = 1/2, prior.absent = 0} i.e. the
+#'   beta). The default is \code{prior.alpha = prior.beta = 1/2} i.e. the
 #'   uninformative "Jeffrey's" prior. Another popular uninformative choice is
 #'   \code{prior.alpha = prior.beta = 1}, i.e. a uniform prior.
+#'   \code{prior.absent} is included for consistency with \code{PoolPrev}, but
+#'   is currently ignored
 #' @param alpha The confidence level to be used for the confidence and credible
 #'   intervals. Defaults to 0.5\% (i.e. 95\% intervals)
 #' @param verbose Logical indicating whether to print progress to screen.
@@ -55,7 +55,8 @@
 
 
 HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
-                         prior.alpha = 0.5, prior.beta = 0.5, prior.absent = 0,
+                         prior.alpha = 0.5, prior.beta = 0.5,
+                         prior.absent = 0,
                          alpha=0.05, verbose = F,cores = 1){
   result <- enquo(result) #The name of column with the result of each test on each pooled sample
   poolSize <- enquo(poolSize) #The name of the column with number of bugs in each pool
@@ -76,7 +77,7 @@ HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
     }
     sdata <- list(N = nrow(data), #number of datapoints (pools)
                   L = length(hierarchy), #number of levels of hierarchy
-                  NumGroups = NumGroups, #Number of groups at each level of hierarchy
+                  NumGroups = array(NumGroups), #Number of groups at each level of hierarchy
                   TotalGroups = sum(NumGroups),
                   #Result = array(data$Result), #PERHAPS TRY REMOVING COLUMN NAMES?
                   Result = dplyr::select(data, !! result)[,1] %>% as.matrix %>% as.numeric %>% array, #This seems a rather obscene way to select a column, but other more sensible methods have inexplicible errors when passed to rstan::sampling

### 2020-09-17 R/PoolReg.R

@@ -33,7 +33,7 @@
 
 
 
-PoolReg <- function (data, formula, poolSize){
+PoolReg <- function (formula, data, poolSize){
   poolSize <- enquo(poolSize)
 
   AllVars <- all.vars(formula)
@@ -56,7 +56,7 @@ PoolReg <- function (data, formula, poolSize){
   # This method of determining whether a formula has any random/mixed effects
   # is pretty much lifted straight from lme4
   if(!length(findbars(formula[[length(formula)]]))){
-    print("Model has no group/random effects. Using a fixed effect (glm)")
+    print("Model has no group/random effects. Using a fixed effect model (glm)")
     out <- glm(formula,
                family = binomial(PoolLink(poolSize)),
                data = data)

### 2020-09-17 R/PoolRegBayes.R

@@ -26,7 +26,7 @@
 
 
 
-PoolRegBayes <- function (data, formula, poolSize, cores = 4, ...){
+PoolRegBayes <- function (formula, data, poolSize, prior = NULL, cores = 4, ...){
   poolSize <- enquo(poolSize)
   AllVars <- all.vars(formula)
 
@@ -56,15 +56,9 @@ PoolRegBayes <- function (data, formula, poolSize, cores = 4, ...){
 
   bform <- bf(f1,f2,nl = TRUE)
 
-  print(get_prior(bform,data = data))
-
-  prior <- set_prior("normal(0,100)", class = "b", nlpar = "eta") #+
-              #prior_string("nlp_eta ~ normal(-4,3)", check = FALSE)) ## Fairly informative prior on the prevalence at every site (rather than on the intercept). This might result in strange 'biases'.
-
-  print(make_stancode(bform,
-                      family = bernoulli("identity"),
-                      data = data,
-                      prior = prior))
+  if(is.null(prior)){
+    prior <- set_prior("normal(0,100)", class = "b", nlpar = "eta")
+  }
 
   model <- brm(bform,
                family = bernoulli("identity"),

### 2020-10-19 paper/Paper.Rmd
Generalise getPrevalence and Prepare for CRAN submission

@@
 library(PoolTestR)
+library(dplyr)
 ```
@@
 HierPrevs <- getPrevalence(HierPrevModel)
-head(HierPrevs)
 
@@
 ```
+
+```{r PrevByVillage, include=FALSE, cache=TRUE}
+PrevVillage <- PoolPrev(Data, Result, PoolSize, Region, Village)
+```
+
 ```{r HierComparisonVillage, echo=FALSE, warning = FALSE}

### 2020-10-19 R/ExamplePoolData.R

@@ -1,0 +1,18 @@
+#' A synthetic dataset for pooled testing
+#'
+#'
+#' The synthetic dataset consisting of pools (sizes 1, 5, or 10) taken from 4 different
+#' regions and 3 different years. Within eaach region specimens are collected
+#' at 4 different villages, and within each village specimens are collected at 8
+#' different sites.
+#'
+#' @format A data frame with 1152 rows and 6 variables:
+#' \describe{
+#'   \item{NumInPool}{Number of specimens in pool. Takes values 1, 5, or 10.}
+#'   \item{Region}{ID of the region the pool was taken from. "A", "B", "C", or "D"}
+#'   \item{Village}{ID of village pool was taken from. Includes name of region e.g. "B-3" is village 3 from region B}
+#'   \item{Site}{ID of village pool was taken from. Includes name of region and village e.g. "B-3-7" is  site 7 from village 3 from region B}
+#'   \item{Result}{Result of test on pool; 0 = negative, 1 = positive}
+#'   \item{Year}{Year of sampling. Years are 0, 1, or 2}
+#' }
+"ExamplePoolData"

### 2020-10-19 R/HierPoolPrev.R

@@ -39,6 +39,8 @@
 #'   intervals. Defaults to 0.5\% (i.e. 95\% intervals)
 #' @param verbose Logical indicating whether to print progress to screen.
 #'   Defaults to false (no printing to screen)
+#' @param cores The number of CPU cores to be used. For fastest results you can
+#'   use all cores by setting \code{cores = parallel::detectCores()}
 #' @return A \code{data.frame} with columns: \itemize{ \item{\code{PrevMLE} (the
 #'   Maximum Likleihood Estimate of prevelance)} \item{\code{CILow} and
 #'   \code{CIHigh} (Lower and Upper Confidence intervals using the Likelihood
@@ -58,17 +60,17 @@ HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
                          prior.alpha = 0.5, prior.beta = 0.5,
                          prior.absent = 0,
                          alpha=0.05, verbose = F,cores = 1){
-  result <- enquo(result) #The name of column with the result of each test on each pooled sample
-  poolSize <- enquo(poolSize) #The name of the column with number of bugs in each pool
-  group_var <- enquos(...) #optional name(s) of columns with other variable to group by. If ommitted uses the complete dataset of pooled sample results to calculate a single prevalence
+  result <- dplyr::enquo(result) #The name of column with the result of each test on each pooled sample
+  poolSize <- dplyr::enquo(poolSize) #The name of the column with number of bugs in each pool
+  group_var <- dplyr::enquos(...) #optional name(s) of columns with other variable to group by. If ommitted uses the complete dataset of pooled sample results to calculate a single prevalence
 
   if(length(group_var) == 0){ #if there are no grouping variables
 
     #Make the model matrix for the group effects - there might be a simpler way of doing this...
     G <- data[,hierarchy,drop = F] %>%
-      mutate_all(as.factor) %>%
+      dplyr::mutate_all(as.factor) %>%
       droplevels %>%
-      mutate_all(as.integer)
+      dplyr::mutate_all(as.integer)
     NumGroups <- G %>% sapply(max)
     G <- t(t(G) + cumsum(NumGroups) - NumGroups)
     Z <- matrix(0,nrow = nrow(data), ncol = sum(NumGroups))
@@ -88,26 +90,26 @@ HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
                   PriorBeta = prior.beta
     )
[…]

### 2020-10-19 R/PoolLink.R

@@ -9,16 +9,17 @@
 #'
 #' @example examples/LogisticRegression.R
 
-#Turns out the pooled sampled regression is equivalent to the problem of monitering bird nests!
-#This is in fact THE EXAMPLE given in glm for adding a custom link function! HA!
+#Turns out the pooled sampled regression is very similar to the problem of
+#monitoring bird nests which is in fact THE EXAMPLE given in glm for adding a
+#custom link function!
 
 PoolLink <- function(PoolSize = 1)
 {
-  linkfun <- function(mu) qlogis(1-(1-mu)^(1/PoolSize))
-  linkinv <- function(eta) 1-(1-plogis(eta))^PoolSize
-  mu.eta  <- function(eta) PoolSize * (1-plogis(eta))^(PoolSize-1) * binomial()$mu.eta(eta)
+  linkfun <- function(mu) stats::qlogis(1-(1-mu)^(1/PoolSize))
+  linkinv <- function(eta) 1-(1-stats::plogis(eta))^PoolSize
+  mu.eta  <- function(eta) PoolSize * (1-stats::plogis(eta))^(PoolSize-1) * stats::binomial()$mu.eta(eta)
   valideta <- function(eta) TRUE
-  link <- "PooledTests"
+  link <- "PooledTestsLogistic"
   structure(list(linkfun = linkfun, linkinv = linkinv,
                  mu.eta = mu.eta, valideta = valideta, name = link),
             class = "link-glm")

### 2020-10-19 R/PoolPrev.R

@@ -1,49 +1,60 @@
 #' Estimation of prevalence based on presence/absence tests on pooled samples
 #'
 #' @export
-#' @param data A \code{data.frame} with one row for each pooled sampled and columns for
-#'             the size of the pool (i.e. the number of specimens / isolates / insects
-#'             pooled to make that particular pool), the result of the test of the pool.
-#'             It may also contain additional columns with additional information (e.g.
-#'             location where pool was taken) which can optionally be used for splitting
-#'             the data into smaller groups and calculting prevalence by group (e.g.
-#'             calculating prevalence for each location)
-#' @param result The name of column with the result of each test on each pooled sample.
-#'                   The result must be stored with 1 indicating a positive test result and
-#'                   0 indicating a negative test result.
-#' @param poolSize The name of the column with number of specimens/isolates/insects in each pool
+#' @param data A \code{data.frame} with one row for each pooled sampled and
+#'   columns for the size of the pool (i.e. the number of specimens / isolates /
+#'   insects pooled to make that particular pool), the result of the test of the
+#'   pool. It may also contain additional columns with additional information
+#'   (e.g. location where pool was taken) which can optionally be used for
+#'   splitting the data into smaller groups and calculting prevalence by group
+#'   (e.g. calculating prevalence for each location)
+#' @param result The name of column with the result of each test on each pooled
+#'   sample. The result must be stored with 1 indicating a positive test result
+#'   and 0 indicating a negative test result.
+#' @param poolSize The name of the column with number of
+#'   specimens/isolates/insects in each pool
 #' @param ... Optional name(s) of columns with variables to group the data by.
-#'            If ommitted the complete dataset is used to estimate a single prevalence.
-#'            If included prevalence is estimated spearately for each group defined by these columns
-#' @param prior.alpha,prior.beta,prior.absent The prior on the prevalence in each group takes the
-#'        form of beta distribution (with parameters alpha and beta) modified to have a point mass of zero
-#'        i.e. allowing for some prior proability that the true prevalence is exactly zero (prior.absent)
[…]

### 2020-10-19 R/PoolReg.R

@@ -1,16 +1,13 @@
-#' Frequentist Mixed or Fixed Effect Logistic Regression with Presence/Absence Tests on
-#' Pooled Samples
+#' Frequentist Mixed or Fixed Effect Logistic Regression with Presence/Absence
+#' Tests on Pooled Samples
 #'
 #' It can be useful to do mixed effects logistic regression on the
 #' presence/absence results from pooled samples, however one must adjust for the
 #' size of each pool to correctly identify trends and associations. This can
-#' done using \code{glmer} from the \code{lme4} package and the custom link
-#' function \code{\link{PoolLink}}, defined in this package.
-#' \code{PoolLogitRegMixed} is provided as a more convenient way to fit the same
-#' model. \code{PoolLogitReg} is similar but for the case with only
-#' population/fixed effects. \code{PoolLogitRegMixed} should be used whenever
-#' there is some heirarchical structure to te sampling frame, or in other cases
-#' where a model with group/random effects is appropriate.
+#' done by using a custom link function [PoolTestR::PoolLink()], defined in this
+#' package, in conjuctions with using \code{glm} from the \code{stats} package
+#' (fixed effect models) or \code{glmer} from the \code{lme4} package (mixed
+#' effect models).
 #'
 #' @export
 #' @param data A \code{data.frame} with one row for each pooled sampled and
@@ -24,47 +21,47 @@
 #'   \code{lme4}, which are generalisation of the formulae used in \code{lm} or
 #'   \code{glm} that allow for random/group effects. The left-hand side of the
 #'   formula should be the name of column in \code{data} with the result of the
-#'   test on the pooled samples. The result must be stored with 1 indicating a
+#'   test on the pooled samples. The result must be encoded with 1 indicating a
 #'   positive test result and 0 indicating a negative test result.
 #' @return An object of class \code{glmerMod} (or \code{glm} if there are no
 #'   random/group effects)
 #'
-#' @example examples/LogisticRegression.R!!!
+#' @example examples/LogisticRegression.R
 
 
 
 PoolReg <- function (formula, data, poolSize){
-  poolSize <- enquo(poolSize)
+  poolSize <- dplyr::enquo(poolSize)
 
   AllVars <- all.vars(formula)
 
-  if(!(as_label(poolSize) %in% colnames(data))){
+  if(!(dplyr::as_label(poolSize) %in% colnames(data))){
     stop("poolSize does not match any of the variable names in the the data provided.")
   }
[…]

### 2020-10-19 R/PoolRegBayes.R

@@ -14,20 +14,27 @@
 #' @param poolSize The name of the column with number of specimens / isolates /
 #'   insects in each pool.
 #' @param formula A \code{formula} of the kind used to define models in
-#'   \code{brms}, which are generalisation of the formulae used in \code{lm,glm}
-#'   or \code{lme4}. The left-hand side of the formula should be the name of
-#'   column in \code{data} with the result of the test on the pooled samples.
+#'   \code{brms}, which are generalisation of the formulae used in \code{lm,
+#'   glm} or \code{lme4}. The left-hand side of the formula should be the name
+#'   of column in \code{data} with the result of the test on the pooled samples.
 #'   The result must be stored with 1 indicating a positive test result and 0
 #'   indicating a negative test result.
-#' @param ... Arguments to be passed brms.
+#' @param prior The priors to be used for the regression parameters. Defaults to
+#'   a non-informative (normal(0,100)) prior on linear coefficients and a
+#'   zero-truncated student-t prior on the group effect standard deviations.
+#'   Custom priors must \code{brmsprior} objects produced by [brms::set_prior()].
+#' @param cores The number of CPU cores to be used. For fastest results you can
+#'   use all cores by setting \code{cores = parallel::detectCores()}
+#' @param ... Additional arguments to be passed to brms.
 #' @return An object of class \code{brms} with the regression outputs.
 #'
-#' @example examples/LogisticRegression.R!!!
+#' @seealso [PoolTestR::PoolReg()], [PoolTestR::getPrevalence()]
+#' @example examples/LogisticRegression.R
 
 
 
 PoolRegBayes <- function (formula, data, poolSize, prior = NULL, cores = 4, ...){
-  poolSize <- enquo(poolSize)
+  poolSize <- dplyr::enquo(poolSize)
   AllVars <- all.vars(formula)
 
   if(!all(AllVars %in% colnames(data))){
@@ -35,7 +42,7 @@ PoolRegBayes <- function (formula, data, poolSize, prior = NULL, cores = 4, ...)
          paste(AllVars[!(AllVars %in% colnames(data))], collapse = ", "))
   }
 
-  if(!(as_label(poolSize) %in% colnames(data))){
+  if(!(dplyr::as_label(poolSize) %in% colnames(data))){
     stop("poolSize does not match any of the variable names in the the data provided.")
   }
 
[…]

### 2020-10-19 R/PoolTestR-package.R

@@ -13,17 +13,10 @@
 #' @name PoolTestR-package
 #' @aliases PoolTestR
 #' @useDynLib PoolTestR, .registration = TRUE
-#' @import dplyr
+#' @importFrom dplyr %>%
 #' @import methods
 #' @import Rcpp
 #' @import rstan
-#' @import lme4
-#' @import brms
-#' @importFrom stats qchisq uniroot quantile model.matrix quantile na.omit terms reformulate
-#' @importFrom parallel detectCores
-#' @importFrom tidyr unite
-#' @importFrom vcd structable
-#' @importFrom stringr str_match_all
 #'
 #' @references
 #' Stan Development Team (2019). RStan: the R interface to Stan. R package version 2.19.2. https://mc-stan.org

### 2020-10-19 R/getPrevalence.R

@@ -1,4 +1,4 @@
-#' Predicting Prevalence from a Bayesian Mixed or Fixed Effect Logistic
+#' Predicting Prevalence from a Mixed or Fixed Effect Logistic
 #' Regression with Presence/Absence Tests on Pooled Samples
 #'
 #' This function works somewhat like a \code{predict} or \code{fitted} generic
@@ -6,13 +6,12 @@
 #' however, as the quantity of interest (prevalence) is neither on the response
 #' or link scale we do not use either of these generic functions. Further, when
 #' the model accounts for the heirarchical structure of the sampling frame (e.g.
-#' Region/Village/Site), it is typical to want to know the predicted values at
+#' Region/Village/Site), it is common to want to know the predicted values at
 #' each level of sampling (e.g. Prevalence at each region, village or site) so
 #' these are calculated automatically.
 #'
 #' @export
-#' @param model An object of class \code{brms} with the regression outputs from
-#'   a call to \code{PoolRegBayes}
+#' @param model An object return by [PoolReg()] or [PoolRegBayes()]
 #' @param data The data for which prevalence needs to be estimated/predicted. If
 #'   not provided, defaults to using the data used to train the model (i.e.
 #'   returns the fitted values of the prevalence)
@@ -21,43 +20,88 @@
 #'   \code{PopulationEffects} contains a \code{data.frame} with the prevalence
 #'   estimated based only the fixed/population effects. When the intercept is
 #'   the only fixed/popultion effect, this is just the population mean (possibly
-#'   adjusted for random/group effects). When there are also
+#'   adjusted for random/group effects). When there are group effects
 #'
-#' @example examples/LogisticRegression.R!!!
+#' @seealso [PoolReg()] and [PoolRegBayes()]
+#' @example examples/LogisticRegression.R
 
-getPrevalence <- function(model,data = model$data){
-  formula <- model$formula$pforms$eta
-  PoolSizeName <- sub(".*\\^", "",as.character(model$formula$formula)[[3]]) #The name of the pool size variable in data
+getPrevalence <- function(model, data = NULL){
+  out <- switch(class(model)[1],
[…]

### 2020-10-19 data-raw/ExamplePoolData.R

@@ -1,0 +1,40 @@
+library(dplyr)
+set.seed(as.integer(as.Date("2020/10/15")))
+
+ExamplePoolData <- expand.grid(NumInPool = c(1,5,10),
+                               Site = as.character(1:8),
+                               Village = as.character(1:4),
+                               Year = 0:2,
+                               Region = c("A","B","C","D")) %>%
+  dplyr::mutate(Village = paste(Region, Village, sep = '-')) %>%
+  dplyr::mutate(Site = paste(Village, Site, sep = '-'))
+
+
+BaseOddsRegion <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+BaseOddsVillage <- rlnorm(length(unique(ExamplePoolData$Village)),sdlog = 0.2)
+names(BaseOddsVillage) <- unique(ExamplePoolData$Village)
+BaseOddsSite <- rlnorm(length(unique(ExamplePoolData$Site)),sdlog = 0.2)
+names(BaseOddsSite) <- unique(ExamplePoolData$Site)
+
+OddsRatioYear <- 0.8
+
+#'True' odds/prevalence in each location
+ExamplePoolData$TrueOdds <- with(ExamplePoolData,
+                                 BaseOddsRegion[Region] *
+                                   BaseOddsVillage[Village] *
+                                   BaseOddsSite[Site] *
+                                   OddsRatioYear^(Year-min(Year)))
+ExamplePoolData$TruePrev <- with(ExamplePoolData, TrueOdds/(1+TrueOdds))
+
+#Simulate test results on pools
+ExamplePoolData$Result <- with(ExamplePoolData,
+                               as.numeric(runif(nrow(ExamplePoolData)) < 1-(1-TruePrev)^NumInPool))
+ExamplePoolData <- ExamplePoolData %>% dplyr::select(-TrueOdds,-TruePrev)
+
+usethis::use_data(ExamplePoolData, overwrite = TRUE)
+
+
+Prev <- PoolPrev(ExamplePoolData, Result, NumInPool, Year, Region)
+#HierPrev <- HierPoolPrev(ExamplePoolData, Result, NumInPool, c('Village', 'Site'), Year, Region)
+Reg <- PoolReg(Result ~ Region + Year + (1|Village/Site), ExamplePoolData, NumInPool)
+#RegBayes <- PoolRegBayes(Result ~ Region + Year + (1|Village/Site), ExamplePoolData, NumInPool)

### 2020-10-19 examples/HierPrevalence.R

@@ -1,0 +1,14 @@
+# Calculate prevalence for a synthetic dataset consisting of pools (sizes 1, 5,
+# or 10) taken from 4 different regions and 3 different years. Within each
+# region specimens are collected at 4 different villages, and within each
+# village specimens are collected at 8 different sites.
+
+\dontrun{
+  #Prevalence for each combination of region and year:
+  #ignoring hierarchical sampling frame within each region
+  PoolPrev(ExamplePoolData, Result, NumInPool, Region, Year)
+  #accounting hierarchical sampling frame within each region
+  HierPoolPrev(ExamplePoolData, Result, NumInPool, c("Village","Site"), Region, Year)
+}
+
+

### 2020-10-19 examples/LogisticRegression.R

@@ -1,54 +1,73 @@
-### Create a simulated dataset with 4 locations across 5 years, where prevalence is declining
-NumPools <- 1000
-#Odds that individual sample is positive in each location in the first year
-BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
-OddsRatioYear <- 0.8
-#Randomly distribute pools between the 4 locations and 5 years,
-#and chose random pool sizes between 10 and 25
-Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
-                   Year = sample(c(0:4), NumPools, replace = T),
-                   NumInPool = sample(10:25, NumPools, replace = T))
-#'True' odds/prevalence in each location
-Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
-Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
-#Simulate test results on pools
-Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
+# Perform logistic-type regression modelling for a synthetic dataset consisting
+# of pools (sizes 1, 5, or 10) taken from 4 different regions and 3 different
+# years. Within each region specimens are collected at 4 different villages,
+# and within each village specimens are collected at 8 different sites.
 
-### Fit modified logistic regression model
 
-#The below two lines produce identical results and support all the same methods
-Reg <- PoolLogitReg(Data,
-                    Result ~ Place + Year,
-                    NumInPool)
-Reg.glm <- glm(Result ~ Place + Year,
-               data = Data,
-               family = binomial(PoolLink(Data$NumInPool)))
-#View summary of model
-summary(Reg)
+### Models in a frequentist framework
+#ignoring hierarchical sampling frame within each region
+Mod <- PoolReg(Result ~ Region + Year,
+               data = ExamplePoolData,
+               poolSize = NumInPool)
+summary(Mod)
 
-#Estimate and confidence intervals for the base odds and odds ratios
-#These should be approx 0.16 for the intercept (i.e. Place A, Year 0),
-#0.25, 0.0625, and 1.0 for places B-D and 0.8 for Year
-exp(cbind(Estimate = coefficients(Reg), confint(Reg)))
+#accounting hierarchical sampling frame within each region
+HierMod <- PoolReg(Result ~ Region + Year + (1|Village/Site),
+                   data = ExamplePoolData,
+                   poolSize = NumInPool)
+summary(HierMod)
[…]

### 2020-10-19 examples/LogisticRegressionOld.R

@@ -1,0 +1,65 @@
+### Create a simulated dataset with 4 locations across 5 years, where prevalence is declining
+NumPools <- 1000
+#Odds that individual sample is positive in each location in the first year
+BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+OddsRatioYear <- 0.8
+#Randomly distribute pools between the 4 locations and 5 years,
+#and chose random pool sizes between 10 and 25
+Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = TRUE),
+                   Year = sample(c(0:4), NumPools, replace = TRUE),
+                   NumInPool = sample(10:25, NumPools, replace = TRUE))
+#'True' odds/prevalence in each location
+Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
+Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
+#Simulate test results on pools
+Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
+
+### Fit modified logistic regression model
+
+#The below two lines produce identical results and support all the same methods
+Reg <- PoolReg(Result ~ Place + Year,
+               data = Data,
+               NumInPool)
+Reg.glm <- glm(Result ~ Place + Year,
+               data = Data,
+               family = binomial(PoolLink(Data$NumInPool)))
+#View summary of model
+summary(Reg)
+
+#Estimate and confidence intervals for the base odds and odds ratios
+#These should be approx 0.16 for the intercept (i.e. Place A, Year 0),
+#0.25, 0.0625, and 1.0 for places B-D and 0.8 for Year
+exp(cbind(Estimate = coefficients(Reg), confint(Reg)))
+
+#Compare the predicted prevalence at each location and time
+Comparison <-  unique(dplyr::select(Data, Place, Year, TruePrev))
+Comparison <- Comparison[with(Comparison,order(Place, Year)),]
+
+Comparison$PredictPrev <- plogis(predict(Reg, newdata = Comparison))
+Comparison
+
+#You can also use the fitted model to predict the odds/prevalence at other times:
+
+#Generate a set of times and places to predict on - note that we don't need to
+#provide pool sizes for the new data as we are predicting the prevalence in
+#individual specimens
+DataPredict <- expand.grid(Place = c("A","B","C","D"),
+                           Year = seq(2,3,by = 0.2))
+#Predicted odds at the new times
[…]

### 2020-10-19 examples/Prevalence.R

@@ -1,14 +1,16 @@
-#Build a synthetic dataset with 1000 pools taken from 4 different locations and 3 different times
-Data <- data.frame(Place = sample(c("A","B","C","D"),1000, replace = TRUE),
-                   Date = sample(as.Date(c("2000/1/1","2001/1/1","2002/1/1")),1000, replace = TRUE),
-                   NumInPool = sample(1:10,1000, replace = TRUE),
-                   Result = sample(0:1,1000,replace = TRUE)
-)
+#Try out on a synthetic dataset consisting of pools (sizes 1, 5, or 10) taken
+#from 4 different regions and 3 different years. Within eaach region specimens
+#are collected at 4 different villages, and within each village specimens are
+#collected at 8 different sites.
+
+\dontrun{
 #Prevalence across the whole (synthetic) dataset
-PoolPrev(Data, Result, NumInPool)
-#Prevalence at each location
-PoolPrev(Data, Result, NumInPool, Place)
-#Prevalence for each time period
-PoolPrev(Data, Result, NumInPool, Date)
-#Prevalence for each combination of location and time-period
-PoolPrev(Data, Result, NumInPool, Place, Date)
+PoolPrev(ExamplePoolData, Result, NumInPool)
+#Prevalence in each Region
+PoolPrev(ExamplePoolData, Result, NumInPool, Region)
+#Prevalence for each year
+PoolPrev(ExamplePoolData, Result, NumInPool, Year)
+#Prevalence for each combination of region and year
+PoolPrev(ExamplePoolData, Result, NumInPool, Region, Year)
+}
+

### 2020-10-19 src/stanExports_BayesianPoolScreen.h

@@ -18,7 +18,7 @@
 #define MODELS_HPP
 #define STAN__SERVICES__COMMAND_HPP
 #include <rstan/rstaninc.hpp>
-// Code generated by Stan version 2.19.1
+// Code generated by Stan version 2.21.0
 #include <stan/model/model_header.hpp>
 namespace model_BayesianPoolScreen_namespace {
 using std::istream;
@@ -37,7 +37,8 @@ stan::io::program_reader prog_reader__() {
     return reader;
 }
 #include <stan_meta_header.hpp>
-class model_BayesianPoolScreen : public prob_grad {
+class model_BayesianPoolScreen
+  : public stan::model::model_base_crtp<model_BayesianPoolScreen> {
 private:
         int N;
         std::vector<int> Result;
@@ -47,13 +48,13 @@ private:
 public:
     model_BayesianPoolScreen(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
-        : prob_grad(0) {
+        : model_base_crtp(0) {
         ctor_body(context__, 0, pstream__);
     }
     model_BayesianPoolScreen(stan::io::var_context& context__,
         unsigned int random_seed__,
         std::ostream* pstream__ = 0)
-        : prob_grad(0) {
+        : model_base_crtp(0) {
         ctor_body(context__, random_seed__, pstream__);
     }
     void ctor_body(stan::io::var_context& context__,
@@ -342,7 +343,7 @@ public:
       for (int i = 0; i < vars.size(); ++i)
         vars(i) = vars_vec[i];
     }
-    static std::string model_name() {
+    std::string model_name() const {
         return "model_BayesianPoolScreen";
     }
     void constrained_param_names(std::vector<std::string>& param_names__,
@@ -384,4 +385,13 @@ public:
 }; // model
 }  // namespace
 typedef model_BayesianPoolScreen_namespace::model_BayesianPoolScreen stan_model;
+#ifndef USING_R
+stan::model::model_base& new_model(
+        stan::io::var_context& data_context,
+        unsigned int seed,
+        std::ostream* msg_stream) {
+  stan_model* m = new stan_model(data_context, seed, msg_stream);
+  return *m;
+}
+#endif
 #endif

### 2020-10-19 src/stanExports_HierBayesianPoolScreen.h

@@ -18,7 +18,7 @@
 #define MODELS_HPP
 #define STAN__SERVICES__COMMAND_HPP
 #include <rstan/rstaninc.hpp>
-// Code generated by Stan version 2.19.1
+// Code generated by Stan version 2.21.0
 #include <stan/model/model_header.hpp>
 namespace model_HierBayesianPoolScreen_namespace {
 using std::istream;
@@ -37,7 +37,8 @@ stan::io::program_reader prog_reader__() {
     return reader;
 }
 #include <stan_meta_header.hpp>
-class model_HierBayesianPoolScreen : public prob_grad {
+class model_HierBayesianPoolScreen
+  : public stan::model::model_base_crtp<model_HierBayesianPoolScreen> {
 private:
         int N;
         int L;
@@ -54,13 +55,13 @@ private:
 public:
     model_HierBayesianPoolScreen(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
-        : prob_grad(0) {
+        : model_base_crtp(0) {
         ctor_body(context__, 0, pstream__);
     }
     model_HierBayesianPoolScreen(stan::io::var_context& context__,
         unsigned int random_seed__,
         std::ostream* pstream__ = 0)
-        : prob_grad(0) {
+        : model_base_crtp(0) {
         ctor_body(context__, random_seed__, pstream__);
     }
     void ctor_body(stan::io::var_context& context__,
@@ -447,7 +448,7 @@ public:
       for (int i = 0; i < vars.size(); ++i)
         vars(i) = vars_vec[i];
     }
-    static std::string model_name() {
+    std::string model_name() const {
         return "model_HierBayesianPoolScreen";
     }
     void constrained_param_names(std::vector<std::string>& param_names__,
@@ -501,4 +502,13 @@ public:
 }; // model
 }  // namespace
 typedef model_HierBayesianPoolScreen_namespace::model_HierBayesianPoolScreen stan_model;
+#ifndef USING_R
+stan::model::model_base& new_model(
+        stan::io::var_context& data_context,
+        unsigned int seed,
+        std::ostream* msg_stream) {
+  stan_model* m = new stan_model(data_context, seed, msg_stream);
+  return *m;
+}
+#endif
 #endif

### 2020-10-19 test/HierarchicalExamples.R

@@ -229,7 +229,7 @@ PredData <- memPool %>%
   unique
 pred <- PredData
 for(n in 1:NGroupTerms){
-  GroupEffectForm <- reformulate(paste0("(",as.character(GroupTerms[(NGroupTerms-n+1):NGroupTerms]),")"))
+  GroupEffectForm <- stats::reformulate(paste0("(",as.character(GroupTerms[(NGroupTerms-n+1):NGroupTerms]),")"))
 
   Prev = predict(memPool,
                  type = 'link',

### 2020-10-19 R/getPrevalence.R
Eliminated error generated by getPrevalence.brmsfit

@@ -11,7 +11,7 @@
 #' these are calculated automatically.
 #'
 #' @export
-#' @param model An object return by [PoolReg()] or [PoolRegBayes()]
+#' @param model An object returned by [PoolReg()] or [PoolRegBayes()]
 #' @param data The data for which prevalence needs to be estimated/predicted. If
 #'   not provided, defaults to using the data used to train the model (i.e.
 #'   returns the fitted values of the prevalence)
@@ -101,7 +101,7 @@ getPrevalence.glmerMod <- function(model, data = NULL){
   if(length(PopTerms)){
     predlist <- list(cbind(PredDataSub,Prev))
   }else{
-    predlist <- list(cbind(PredDataSub[,!names(PredDataSub) == "DummyVar"],Prev))
+    predlist <- list(cbind(PredDataSub[,!names(PredDataSub) == "DummyVar", drop = FALSE],Prev))
   }
 
   #Make predictions based on group effects
@@ -151,34 +151,36 @@ getPrevalence.brmsfit <- function(model, data = NULL){
   }else{
     PredDataSub <- data.frame(DummyVar = 1)
   }
-  PredDataSub[,PoolSizeName] = 1 #Setting PoolSize to 1 means that the response scale is the same as the prevalence scale
+  PredDataSub[,PoolSizeName] <- 1 #Setting PoolSize to 1 means that the response scale is the same as the prevalence scale
   rownames(PredDataSub) <- NULL
   Prev <- stats::fitted(model,
                  scale = 'response',
                  re_formula = NA,
                  newdata = PredDataSub) %>%
     as.data.frame %>%
-    dplyr::select(-dplyr::one_of(c("Est.Error","DummyVar",PoolSizeName))) %>%
+    dplyr::select(-dplyr::any_of(c("Est.Error","DummyVar"))) %>%
     stats::setNames(c("Estimate", "CrILow", "CrIHigh"))
 
-  predlist <- list(cbind(PredDataSub,Prev))
+  predlist <- list(cbind(dplyr::select(PredDataSub,-dplyr::any_of(PoolSizeName)),
+                         Prev))
 
   #Make predictions based on group effects
   if(NGroupTerms){
     for(n in 1:NGroupTerms){
       PredDataSub <-  PredData[,c(PopTerms,GroupTermNames[1:n]),drop =F] %>% unique
-      PredDataSub[,PoolSizeName] = 1 #Setting PoolSize to 1 means that the response scale is the same as the prevalence scale
[…]

### 2020-10-27 R/ExampleData.R
Extend getPrevalence to work for more general random effect models, add example data set, add progress bars

@@ -1,0 +1,43 @@
+#' A synthetic dataset for pooled testing
+#'
+#'
+#' A synthetic dataset mimimicing a realistic hierarachical sampling frame.
+#' Simulated samples are taken from across three regions (A, B, and C) in which
+#' the vectors have a low (0.5\%), medium (2\%), and high (4\%) prevalence of
+#' the marker of interest. Ten villages are chosen within each region, and traps
+#' are placed at ten sites within each village. Every site is sampled once a
+#' year over three years (0, 1, and 2). Prevalence is not uniform within each
+#' region or over time. At baseline (year 0), prevalence varies between villages
+#' within each region around the mean for the region, and prevalence varies
+#' between sites within each village around the mean for the village.
+#' Consequently though the prevalence is different for each site, two sites
+#' within the same village are likely to have a more similar prevalence than two
+#' sites in different villages, or two sites in different regions. On average
+#' the prevalence is declining over time (odds ratio of 0.8 per year), however,
+#' the growth rate varies between villages. Consequently two sites in different
+#' villages with similar prevalence at baseline may have different prevalence by
+#' the third year, and prevalence may go up in some villages. Each year the
+#' traps at each site catch a negative binomial number (mean 200, dispersion 5)
+#' of vectors. The catch size at each site and year is independent. Each year,
+#' the catches at each site are pooled into groups of 25 with an additional pool
+#' for any remainder (e.g. a catch of 107 vectors will be pooled into 4 pools of
+#' 25 and one pool of 7). Test results on each pool are simulated assuming the
+#' test has perfect sensitivity and specificity.
+#'
+#' The 'true' model can be summarised in formula notation as:
+#'
+#' Result ~ Region + Year + (1+Year|Village) + (1|Site)
+#'
+#' where the coefficient for Year is log(0.8), the standard deviation for
+#' intercept random effects for village and site are both 0.5, the standard
+#' deviation for the year random effect for village is 0.2 and the random
+#' effects are all uncorrelated/independent.
+#'
+#' @format A data frame with 6 variables: \describe{
+#'   \item{NumInPool}{Number of specimens in pool. Range = 1:25}
+#'   \item{Region}{ID of the region the pool was taken from. "A", "B", or "C"}
+#'   \item{Village}{ID of village pool was taken from. Includes name of region e.g. "B-3" is village 3 from region B}
[…]

### 2020-10-27 R/ExamplePoolData.R

@@ -1,18 +1,0 @@
-#' A synthetic dataset for pooled testing
-#'
-#'
-#' The synthetic dataset consisting of pools (sizes 1, 5, or 10) taken from 4 different
-#' regions and 3 different years. Within eaach region specimens are collected
-#' at 4 different villages, and within each village specimens are collected at 8
-#' different sites.
-#'
-#' @format A data frame with 1152 rows and 6 variables:
-#' \describe{
-#'   \item{NumInPool}{Number of specimens in pool. Takes values 1, 5, or 10.}
-#'   \item{Region}{ID of the region the pool was taken from. "A", "B", "C", or "D"}
-#'   \item{Village}{ID of village pool was taken from. Includes name of region e.g. "B-3" is village 3 from region B}
-#'   \item{Site}{ID of village pool was taken from. Includes name of region and village e.g. "B-3-7" is  site 7 from village 3 from region B}
-#'   \item{Result}{Result of test on pool; 0 = negative, 1 = positive}
-#'   \item{Year}{Year of sampling. Years are 0, 1, or 2}
-#' }
-"ExamplePoolData"

### 2020-10-27 R/HierPoolPrev.R

@@ -59,7 +59,7 @@
 HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
                          prior.alpha = 0.5, prior.beta = 0.5,
                          prior.absent = 0,
-                         alpha=0.05, verbose = F,cores = 1){
+                         alpha=0.05, verbose = F,cores = 4){
   result <- dplyr::enquo(result) #The name of column with the result of each test on each pooled sample
   poolSize <- dplyr::enquo(poolSize) #The name of the column with number of bugs in each pool
   group_var <- dplyr::enquos(...) #optional name(s) of columns with other variable to group by. If ommitted uses the complete dataset of pooled sample results to calculate a single prevalence
@@ -116,19 +116,23 @@ HierPoolPrev <- function(data,result,poolSize,hierarchy,...,
 
     out
   }else{ #if there are grouping variables the function calls itself iteratively on each group
-    out <- data %>%
-      dplyr::group_by(!!! group_var) %>%
-      dplyr::group_modify(function(x,...){
-        HierPoolPrev(x,!! result,!! poolSize,
-                     hierarchy,
-                     prior.alpha = prior.alpha,
-                     prior.beta = prior.beta,
-                     prior.absent = prior.absent,
-                     alpha=alpha,
-                     verbose = verbose,
-                     cores = cores)}) %>%
+    data <- data %>%
+      dplyr::group_by(!!! group_var)
+    nGroups <- dplyr::n_groups(data)
+    ProgBar <- progress::progress_bar$new(format = "[:bar] :current/:total (:percent)", total = nGroups)
+    ProgBar$tick(-1)
+    out <- data %>% dplyr::group_modify(function(x,...){
+      ProgBar$tick(1)
+      HierPoolPrev(x,!! result,!! poolSize,
+                   hierarchy,
+                   prior.alpha = prior.alpha,
+                   prior.beta = prior.beta,
+                   prior.absent = prior.absent,
+                   alpha = alpha,
+                   verbose = verbose,
+                   cores = cores)}) %>%
       as.data.frame()
-    cat("\n")
+    ProgBar$tick(1)
   }
   dplyr::tibble(out)
 }

### 2020-10-27 R/PoolPrev.R

@@ -51,7 +51,7 @@
 
 PoolPrev <- function(data,result,poolSize,...,
                      prior.alpha = 0.5, prior.beta = 0.5, prior.absent = 0,
-                     alpha = 0.05, verbose = F,cores = 1){
+                     alpha = 0.05, verbose = F,cores = 4){
   result <- dplyr::enquo(result) #The name of column with the result of each test on each pooled sample
   poolSize <- dplyr::enquo(poolSize) #The name of the column with number of bugs in each pool
   group_var <- dplyr::enquos(...) #optional name(s) of columns with other variable to group by. If ommitted uses the complete dataset of pooled sample results to calculate a single prevalence
@@ -177,17 +177,21 @@ PoolPrev <- function(data,result,poolSize,...,
 
     out
   }else{ #if there are grouping variables the function calls itself iteratively on each group
-    out <- data %>%
-      dplyr::group_by(!!! group_var) %>%
-      dplyr::group_modify(function(x,...){
-        PoolPrev(x,!! result,!! poolSize,
-                 alpha=alpha,verbose = verbose,
-                 prior.absent = prior.absent,
-                 prior.alpha = prior.alpha,
-                 prior.beta = prior.beta,
-                 cores = cores)}) %>%
+    data <- data %>%
+      dplyr::group_by(!!! group_var)
+    nGroups <- dplyr::n_groups(data)
+    ProgBar <- progress::progress_bar$new(format = "[:bar] :current/:total (:percent)", total = nGroups)
+    ProgBar$tick(-1)
+    out <- data %>% dplyr::group_modify(function(x,...){
+      ProgBar$tick(1)
+      PoolPrev(x,!! result,!! poolSize,
+               alpha=alpha,verbose = verbose,
+               prior.absent = prior.absent,
+               prior.alpha = prior.alpha,
+               prior.beta = prior.beta,
+               cores = cores)}) %>%
       as.data.frame()
-    cat("\n")
+    ProgBar$tick(1)
   }
   dplyr::tibble(out)
 }

### 2020-10-27 R/PoolReg.R

@@ -23,6 +23,9 @@
 #'   formula should be the name of column in \code{data} with the result of the
 #'   test on the pooled samples. The result must be encoded with 1 indicating a
 #'   positive test result and 0 indicating a negative test result.
+#' @param link Link function. There are two options `'logit'` (logistic
+#'   regression, the default) and `'cloglog'` (complementary log log
+#'   regression).
 #' @return An object of class \code{glmerMod} (or \code{glm} if there are no
 #'   random/group effects)
 #'
@@ -30,39 +33,54 @@
 
 
 
-PoolReg <- function (formula, data, poolSize){
-  poolSize <- dplyr::enquo(poolSize)
+PoolReg <- function (formula, data, poolSize, link = 'logit'){
+  poolSize <- deparse(substitute(poolSize))
 
   AllVars <- all.vars(formula)
 
-  if(!(dplyr::as_label(poolSize) %in% colnames(data))){
+  if(!(poolSize %in% colnames(data))){
     stop("poolSize does not match any of the variable names in the the data provided.")
   }
-  poolSize <- dplyr::select(data,!! poolSize)[,1]
-
   if(!all(AllVars %in% colnames(data))){
     stop("formula contains variables that aren't in the data: ",
          paste(AllVars[!(AllVars %in% colnames(data))], collapse = ", "))
   }
-  if(dplyr::as_label(poolSize) %in% AllVars){
-    stop("The size of the pools (",dplyr::as_label(poolSize),")",
+  if(poolSize %in% AllVars){
+    stop("The size of the pools (",poolSize,")",
          "is included as a variable in the regression formula. ",
          "Are you sure this is what you meant to do?")
+  }
+
+  if(link == "cloglog"){
+    formula <- stats::update(formula, formula(paste0("~. + offset(log(",poolSize,"))")))
   }
 
   # This method of determining whether a formula has any random/mixed effects
   # is pretty much lifted straight from lme4
   if(!length(lme4::findbars(formula[[length(formula)]]))){
     print("Model has no group/random effects. Using a fixed effect model (glm)")
-    out <- stats::glm(formula,
-                      family = stats::binomial(PoolLink(poolSize)),
-                      data = data)
+    out <- switch(link,
+                  logit = stats::glm(formula,
+                                     family = stats::binomial(PoolLink(data[[poolSize]])),
+                                     data = data),
+                  cloglog = stats::glm(formula,
+                                       family = stats::binomial("cloglog"),
+                                       data = data),
[…]

### 2020-10-27 R/PoolRegBayes.R

@@ -19,10 +19,14 @@
 #'   of column in \code{data} with the result of the test on the pooled samples.
 #'   The result must be stored with 1 indicating a positive test result and 0
 #'   indicating a negative test result.
+#' @param link Link function. There are two options `'logit'` (logistic
+#'   regression, the default) and `'cloglog'` (complementary log log
+#'   regression).
 #' @param prior The priors to be used for the regression parameters. Defaults to
 #'   a non-informative (normal(0,100)) prior on linear coefficients and a
 #'   zero-truncated student-t prior on the group effect standard deviations.
-#'   Custom priors must \code{brmsprior} objects produced by [brms::set_prior()].
+#'   Custom priors must \code{brmsprior} objects produced by
+#'   [brms::set_prior()].
 #' @param cores The number of CPU cores to be used. For fastest results you can
 #'   use all cores by setting \code{cores = parallel::detectCores()}
 #' @param ... Additional arguments to be passed to brms.
@@ -33,16 +37,17 @@
 
 
 
-PoolRegBayes <- function (formula, data, poolSize, prior = NULL, cores = 4, ...){
+PoolRegBayes <- function (formula, data, poolSize, link = 'logit', prior = NULL, cores = 4, ...){
   poolSize <- dplyr::enquo(poolSize)
   AllVars <- all.vars(formula)
+  PoolSizeName <- dplyr::as_label(poolSize)
 
   if(!all(AllVars %in% colnames(data))){
     stop("formula contains variables that aren't in the data: ",
          paste(AllVars[!(AllVars %in% colnames(data))], collapse = ", "))
   }
 
-  if(!(dplyr::as_label(poolSize) %in% colnames(data))){
+  if(!(PoolSizeName %in% colnames(data))){
     stop("poolSize does not match any of the variable names in the the data provided.")
   }
 
@@ -50,16 +55,22 @@ PoolRegBayes <- function (formula, data, poolSize, prior = NULL, cores = 4, ...)
     stop("formula contains a variable called eta which is needed internally. ",
          "Please rename this variable and try again")
   }
-  if(dplyr::as_label(poolSize) %in% AllVars){
-    stop("The size of the pools (",dplyr::as_label(poolSize),")",
+  if(PoolSizeName %in% AllVars){
+    stop("The size of the pools (",PoolSizeName,")",
          "is included as a variable in the regression formula. ",
          "Are you sure this is what you meant to do?")
   }
 
[…]

### 2020-10-27 R/SimpleExampleData.R

@@ -1,0 +1,18 @@
+#' A synthetic dataset for pooled testing
+#'
+#'
+#' The simple synthetic dataset consisting of pools (sizes 1, 5, or 10) taken from 4 different
+#' regions and 3 different years. Within eaach region specimens are collected
+#' at 4 different villages, and within each village specimens are collected at 8
+#' different sites.
+#'
+#' @format A data frame with 1152 rows and 6 variables:
+#' \describe{
+#'   \item{NumInPool}{Number of specimens in pool. Takes values 1, 5, or 10.}
+#'   \item{Region}{ID of the region the pool was taken from. "A", "B", "C", or "D"}
+#'   \item{Village}{ID of village pool was taken from. Includes name of region e.g. "B-3" is village 3 from region B}
+#'   \item{Site}{ID of village pool was taken from. Includes name of region and village e.g. "B-3-7" is  site 7 from village 3 from region B}
+#'   \item{Result}{Result of test on pool; 0 = negative, 1 = positive}
+#'   \item{Year}{Year of sampling. Years are 0, 1, or 2}
+#' }
+"SimpleExampleData"

### 2020-10-27 R/TruePrev.R

@@ -1,0 +1,24 @@
+#' A synthetic dataset for pooled testing
+#'
+#'
+#' This dataframe contains the 'true' values of prevalence for each, site, village, region and year used to generate the synthetic dataset \code{ExampleData}
+#'
+#' The 'true' model can be summarised in formula notation as:
+#'
+#' Result ~ Region + Year + (1+Year|Village) + (1|Site)
+#'
+#' where the coefficient for Year is log(0.8), the standard deviation for
+#' intercept random effects for village and site are both 0.5, the standard
+#' deviation for the year random effect for village is 0.2 and the random
+#' effects are all uncorrelated/independent.
+#'
+#' @format A data frame with 900 rows and 7 variables: \describe{
+#'   \item{Region}{ID of the region the pool was taken from. "A", "B", or "C"}
+#'   \item{Village}{ID of village pool was taken from. Includes name of region e.g. "B-3" is village 3 from region B}
+#'   \item{Site}{ID of village pool was taken from. Includes name of region and village e.g. "B-3-7" is site 7 from village 3 from region B}
+#'   \item{Year}{Year of sampling. Years are 0, 1, or 2}
+#'   \item{PrevalenceRegion}{'True' average prevalence in the region (in that year)}
+#'   \item{PrevalenceVillage}{'True' average prevalence in the village (in that year)}
+#'   \item{PrevalenceSite}{'True' prevalence at that site (in that year)}
+#'   }
+"TruePrev"

### 2020-10-27 R/getPrevalence.R

@@ -1,5 +1,5 @@
-#' Predicting Prevalence from a Mixed or Fixed Effect Logistic
-#' Regression with Presence/Absence Tests on Pooled Samples
+#' Predicting Prevalence from a Mixed or Fixed Effect Logistic Regression with
+#' Presence/Absence Tests on Pooled Samples
 #'
 #' This function works somewhat like a \code{predict} or \code{fitted} generic
 #' function returning the model predicted prevalence for a given set of data;
@@ -12,184 +12,276 @@
 #'
 #' @export
 #' @param model An object returned by [PoolReg()] or [PoolRegBayes()]
-#' @param data The data for which prevalence needs to be estimated/predicted. If
-#'   not provided, defaults to using the data used to train the model (i.e.
+#' @param newdata The data for which prevalence needs to be estimated/predicted.
+#'   If not provided, defaults to using the data used to train the model (i.e.
 #'   returns the fitted values of the prevalence)
+#' @param re.form A description of which random effects to inlcude in the
+#'   prediction. If omitted, getPrevalence automatically tests to see if there
+#'   are any random effect terms. If not, it just returns the estimates based on
+#'   population effects. If there are random effects, it tests to see if the
+#'   random effect variables form a nested hierarchical structure. If so, in
+#'   addition to the estimates based on population effects only, it will
+#'   estimate at different levels of the nested hierarhical structure in order
+#'   of increasing granularity. For manual control you can set to NA for
+#'   population effects only, or a onesided formula specifying the form of the
+#'   random effects to include in estimates, or a list of such objects.
 #' @return A \code{list} with at least one field \code{PopulationEffects} and an
 #'   additional field for every random/group effect variable. The field
 #'   \code{PopulationEffects} contains a \code{data.frame} with the prevalence
 #'   estimated based only the fixed/population effects. When the intercept is
 #'   the only fixed/popultion effect, this is just the population mean (possibly
-#'   adjusted for random/group effects). When there are group effects
+#'   adjusted for random/group effects). When there are group effects terms,
[…]

### 2020-10-27 data-raw/ComplexExampleData.R

@@ -1,0 +1,175 @@
+library(dplyr)
+set.seed(as.numeric(as.Date("2020/10/22")))
+RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
+NumRegions <- length(RegionPrevs)
+NumVillages <- 10 #Villages per Region
+NumSites <- 10 #Sites per village
+MeanCatch <- 200 #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
+DispersionCatch <- 5
+MaxPoolSize <- 25
+# Variability between villages and between sites in a given village.
+# We could probably increase these standard deviations to make the difference between the hierarchical and non-hierarchical models more stark
+VillageSD <- 0.5
+SiteSD <- 0.5
+VillageSDTrend <- 0.2
+SiteSDTrend <- 0
+Years <- 0:2
+GrowthRate <- log(0.8)
+
+
+
+ExampleData <- data.frame()
+for(R in names(RegionPrevs)){
+  for(V in 1:NumVillages){
+    #Difference of village prevalence from the region prevalence on log-odds scale
+    VillageDeviate <- rnorm(1, mean = 0, sd = VillageSD)
+    VillageDeviateTrend <- rnorm(1, mean = 0, sd = VillageSDTrend)
+    for(S in 1:NumSites){
+      #Difference of site prevalence from the village prevalence on log-odds scale
+      SiteDeviate <- rnorm(1, mean = 0, sd = SiteSD)
+      SiteDeviateTrend <- rnorm(1, mean = 0, sd = SiteSDTrend)
+
+      for(Y in Years){
+        VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + Y * (GrowthRate + VillageDeviateTrend))
+        SiteTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + SiteDeviate + Y * (GrowthRate + VillageDeviateTrend + SiteDeviateTrend))
+        #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes == 0 to guarantee at least one mossie
+        Catch <- 0
+        while(Catch<=0){
+          Catch <- rnbinom(1, mu = MeanCatch, DispersionCatch)
+        }
+        #Split pools into as many of size MaxPoolSize as possible and the remainder in another small pool
+        NumBigPools <- Catch %/% MaxPoolSize
+        if(NumBigPools){
+          ExampleData <- rbind(ExampleData,
[…]

### 2020-10-27 data-raw/ExamplePoolData.R

@@ -1,40 +1,0 @@
-library(dplyr)
-set.seed(as.integer(as.Date("2020/10/15")))
-
-ExamplePoolData <- expand.grid(NumInPool = c(1,5,10),
-                               Site = as.character(1:8),
-                               Village = as.character(1:4),
-                               Year = 0:2,
-                               Region = c("A","B","C","D")) %>%
-  dplyr::mutate(Village = paste(Region, Village, sep = '-')) %>%
-  dplyr::mutate(Site = paste(Village, Site, sep = '-'))
-
-
-BaseOddsRegion <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
-BaseOddsVillage <- rlnorm(length(unique(ExamplePoolData$Village)),sdlog = 0.2)
-names(BaseOddsVillage) <- unique(ExamplePoolData$Village)
-BaseOddsSite <- rlnorm(length(unique(ExamplePoolData$Site)),sdlog = 0.2)
-names(BaseOddsSite) <- unique(ExamplePoolData$Site)
-
-OddsRatioYear <- 0.8
-
-#'True' odds/prevalence in each location
-ExamplePoolData$TrueOdds <- with(ExamplePoolData,
-                                 BaseOddsRegion[Region] *
-                                   BaseOddsVillage[Village] *
-                                   BaseOddsSite[Site] *
-                                   OddsRatioYear^(Year-min(Year)))
-ExamplePoolData$TruePrev <- with(ExamplePoolData, TrueOdds/(1+TrueOdds))
-
-#Simulate test results on pools
-ExamplePoolData$Result <- with(ExamplePoolData,
-                               as.numeric(runif(nrow(ExamplePoolData)) < 1-(1-TruePrev)^NumInPool))
-ExamplePoolData <- ExamplePoolData %>% dplyr::select(-TrueOdds,-TruePrev)
-
-usethis::use_data(ExamplePoolData, overwrite = TRUE)
-
-
-Prev <- PoolPrev(ExamplePoolData, Result, NumInPool, Year, Region)
-#HierPrev <- HierPoolPrev(ExamplePoolData, Result, NumInPool, c('Village', 'Site'), Year, Region)
-Reg <- PoolReg(Result ~ Region + Year + (1|Village/Site), ExamplePoolData, NumInPool)
-#RegBayes <- PoolRegBayes(Result ~ Region + Year + (1|Village/Site), ExamplePoolData, NumInPool)

### 2020-10-27 data-raw/SimpleExampleData.R

@@ -1,0 +1,34 @@
+library(dplyr)
+set.seed(as.integer(as.Date("2020/10/15")))
+
+SimpleExampleData <- expand.grid(NumInPool = c(1,5,10),
+                               Site = as.character(1:8),
+                               Village = as.character(1:4),
+                               Year = 0:2,
+                               Region = c("A","B","C","D")) %>%
+  dplyr::mutate(Village = paste(Region, Village, sep = '-')) %>%
+  dplyr::mutate(Site = paste(Village, Site, sep = '-'))
+
+
+BaseOddsRegion <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+BaseOddsVillage <- rlnorm(length(unique(SimpleExampleData$Village)),sdlog = 0.2)
+names(BaseOddsVillage) <- unique(SimpleExampleData$Village)
+BaseOddsSite <- rlnorm(length(unique(SimpleExampleData$Site)),sdlog = 0.2)
+names(BaseOddsSite) <- unique(SimpleExampleData$Site)
+
+OddsRatioYear <- 0.8
+
+#'True' odds/prevalence in each location
+SimpleExampleData$TrueOdds <- with(SimpleExampleData,
+                                 BaseOddsRegion[Region] *
+                                   BaseOddsVillage[Village] *
+                                   BaseOddsSite[Site] *
+                                   OddsRatioYear^(Year-min(Year)))
+SimpleExampleData$TruePrev <- with(SimpleExampleData, TrueOdds/(1+TrueOdds))
+
+#Simulate test results on pools
+SimpleExampleData$Result <- with(SimpleExampleData,
+                               as.numeric(runif(nrow(SimpleExampleData)) < 1-(1-TruePrev)^NumInPool))
+SimpleExampleData <- SimpleExampleData %>% dplyr::select(-TrueOdds,-TruePrev)
+
+usethis::use_data(SimpleExampleData, overwrite = TRUE)

### 2020-10-27 examples/HierPrevalence.R

@@ -6,9 +6,9 @@
 \dontrun{
   #Prevalence for each combination of region and year:
   #ignoring hierarchical sampling frame within each region
-  PoolPrev(ExamplePoolData, Result, NumInPool, Region, Year)
+  PoolPrev(SimpleExampleData, Result, NumInPool, Region, Year)
   #accounting hierarchical sampling frame within each region
-  HierPoolPrev(ExamplePoolData, Result, NumInPool, c("Village","Site"), Region, Year)
+  HierPoolPrev(SimpleExampleData, Result, NumInPool, c("Village","Site"), Region, Year)
 }
 
 

### 2020-10-27 examples/LogisticRegression.R

@@ -7,13 +7,13 @@
 ### Models in a frequentist framework
 #ignoring hierarchical sampling frame within each region
 Mod <- PoolReg(Result ~ Region + Year,
-               data = ExamplePoolData,
+               data = SimpleExampleData,
                poolSize = NumInPool)
 summary(Mod)
 
 #accounting hierarchical sampling frame within each region
 HierMod <- PoolReg(Result ~ Region + Year + (1|Village/Site),
-                   data = ExamplePoolData,
+                   data = SimpleExampleData,
                    poolSize = NumInPool)
 summary(HierMod)
 #Extract fitted prevalence for each combination of region and year and then at
@@ -25,18 +25,18 @@ getPrevalence(HierMod)
 ### Models in a Bayesian framework with default (non-informative) priors
 #ignoring hierarchical sampling frame within each region
 \dontrun{
-BayesMod <- PoolRegBayes(Result ~ Region + Year,
-                         data = ExamplePoolData,
-                         poolSize = NumInPool)
-summary(BayesMod)
-getPrevalence(BayesMod) #Extract fitted prevalence for each combination of region and year
+  BayesMod <- PoolRegBayes(Result ~ Region + Year,
+                           data = SimpleExampleData,
+                           poolSize = NumInPool)
+  summary(BayesMod)
+  getPrevalence(BayesMod) #Extract fitted prevalence for each combination of region and year
 
-#accounting hierarchical sampling frame within each region
-BayesHierMod <- PoolRegBayes(Result ~ Region + Year + (1|Village/Site),
-                             data = ExamplePoolData,
-                             poolSize = NumInPool)
-summary(BayesHierMod)
-getPrevalence(BayesHierMod)
+  #accounting hierarchical sampling frame within each region
+  BayesHierMod <- PoolRegBayes(Result ~ Region + Year + (1|Village/Site),
+                               data = SimpleExampleData,
+                               poolSize = NumInPool)
+  summary(BayesHierMod)
+  getPrevalence(BayesHierMod)
 }
 
 ### Calculate adjusted estimates of prevalence
@@ -45,7 +45,7 @@ getPrevalence(BayesHierMod)
 # Extract fitted prevalence for each combination of region and year
 getPrevalence(Mod)
 \dontrun{
-getPrevalence(BayesMod)
+  getPrevalence(BayesMod)
 }
 
 #Extract fitted prevalence for each combination of region and year and then at
[…]

### 2020-10-27 examples/Prevalence.R

@@ -4,13 +4,13 @@
 #collected at 8 different sites.
 
 \dontrun{
-#Prevalence across the whole (synthetic) dataset
-PoolPrev(ExamplePoolData, Result, NumInPool)
-#Prevalence in each Region
-PoolPrev(ExamplePoolData, Result, NumInPool, Region)
-#Prevalence for each year
-PoolPrev(ExamplePoolData, Result, NumInPool, Year)
-#Prevalence for each combination of region and year
-PoolPrev(ExamplePoolData, Result, NumInPool, Region, Year)
+  #Prevalence across the whole (synthetic) dataset
+  PoolPrev(SimpleExampleData, Result, NumInPool)
+  #Prevalence in each Region
+  PoolPrev(SimpleExampleData, Result, NumInPool, Region)
+  #Prevalence for each year
+  PoolPrev(SimpleExampleData, Result, NumInPool, Year)
+  #Prevalence for each combination of region and year
+  PoolPrev(SimpleExampleData, Result, NumInPool, Region, Year)
 }
 

### 2020-10-27 test/Comparisons.R

@@ -1,0 +1,21 @@
+library(dplyr)
+NumPools <- 1000
+#Odds that individual sample is positive in each location in the first year
+BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
+OddsRatioYear <- 0.8
+#Randomly distribute pools between the 4 locations and 5 years,
+#and chose random pool sizes between 10 and 25
+Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
+                   Year = sample(c(0:4), NumPools, replace = T),
+                   NumInPool = sample(10:25, NumPools, replace = T))
+#'True' odds/prevalence in each location
+Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
+Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
+#Simulate test results on pools
+Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
+
+
+DataCount <- with(Data,table(Result, NumInPool)) %>% as.matrix
+DataCount[2,]
+
+binGroup2::propCI(DataCount[1,], as.integer(colnames(DataCount)),colSums(DataCount), ci.method = "exact")

### 2020-10-27 paper/Paper.Rmd
Update .gitignore

--- 2020-08-13 paper/Paper.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(cache.extra = R.version.string)
+knitr::opts_chunk$set(cache.extra = R.version)
+library(PoolTestR)
+library(dplyr)
 ```
+### The PoolTestR Package
 
-[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen]
-
-We wish to estimate the prevalence, p, of a disease or molecular marker in a population from the results of tests on a pooled samples.
-For a pool combining N samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$.
-If $M$ such pools from a single location are tested and $m$ of these are positive the maximum likelihood estimate (MLE) of $q\ is \frac{m}{M}$ and the MLE of the prevalence, $p$, in the population is ${1-\left(1-\frac{m}{M}\right)}^\frac{1}{N}$.
-However, if the pools are of different sizes there is no convenient closed-form expression for the MLE, which must be approximated numerically from the likelihood function.
-With pools of size $N_1,N_2,\ldots$, and tests results $y_1,y_2,\ldots$ (where $y_i$ is zero if the test result is negative and one if positive) the likelihood function is
-
-$L\left(p\middle|y\right)=\prod_{i}{y_i+\left(-1\right)^{y_i}\ \left(1-p\right)^{N_i}}.$
-
-Similarly, Bayesian inference has to performed numerically in most cases.
-However, in the special case where all pool tests are negative and the prior on $p$ has a $Beta(\alpha,\beta)$ distribution, the posterior for $p$ is given by $Beta(\alpha,\beta+\sum_{i}\ N_i)$.
-In some locations there may be some reasonable prior probability that the disease is absent i.e.
-prevalence is exactly zero.
-Thus, we may wish to consider a prior such that $p$ has probability $\gamma$ of being exactly zero and $Beta(\alpha,\beta)$ distributed otherwise.
-If any test results are positive then the posterior probability of absence is zero and the posterior distribution of $p$ is the same as would be reached with an unmodified $Beta(\alpha,\beta)$ prior.
-However, in the case where all test results are negative
-
-$P\left(p=0|y=0,N\right)=\left(1+\frac{\left(1-\gamma\right)B\left(\alpha,\beta+\sum_{i}\ N_i\right)}{\gamma B\left(\alpha,\ \beta\right)}\right)^{-1}$,
-
-where $B(.,.)$ is the beta function.
-
-Prevalence may vary over the different locations, times, and subpopulation from which the samples are taken, so we may wish to use regression analyses model the relationship between prevalence and a set of explanatory variables recorded for each pool.
-We use a logistic regression model adjusted for pool sizes which can be viewed as a kind of generalised linear model.
-Mathematically, our modified logisitic model is similar to Shaffer’s model of bird nesting success rates, which adjusts the logistic model to account for different durations of nest observations (Shaffer, T.
-2004.
-Auk 121(2): 526-540).
-Let $x_{ij}$ be the observed value of dependent variable $j$ for pool $i$ and $x_{i0}=1$.
-A standard unadjusted logistic regression model with intercept $\beta_0$ and parameters $\beta_j$ would model test results as
-
-$y_i |\beta, x_{ij} \sim Bernoulli( logit^{-1} \sum_{j}{x_{ij} \beta_j} )$.
-
-However, with pooled samples we model the results of pooled tests as
-$y_i |\beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1} \sum_{j}{x_{ij} \beta_j} \right)^{N_i}\right)$.
-
-When all pool sizes are one, this simplifies to the standard logistic model. Maximum likelihood estimation and Bayesian inference must be performed numerically from the likelihood function:
-
-$L\left(\beta\middle|y,x,N\right)=\prod_{i}{y_i+\left(-1\right)^{y_i}\ \left(1-logit^{-1}\sum_{j}{x_{ij}\beta_j}\right)^{N_i}}$.
-
-It is common to adopt a hierarchical sampling structure when collecting specimens.
-For instance, if one wishes to estimate the prevalence of a marker in mosquitos,  a common way to collect specimens is to set out mosquito traps.
-To estimate the typical prevalence in a region, one may place traps in a number of randomly or systemtically chosen sites.
-In such cases it would be best to attempt to account for any intra-site variation in prevalence using a hiearachical or mixed-effects modelling framework.
-In the general case let $z_{ik}$ define the design matrix and $u_k$ the group effects for a mixed-effects model.
-Then we model the outcomes as
-
-$y_{i} |u, z_{ik},\beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1}\left(\sum_{k}{z_{ik} u_k} + \sum_{j}{x_{ij} \beta_j}\right) \right)^{N_i}\right)$
-
-$u \sim N(0, \Sigma)$.
-
-For the more specific case of a $K$-level hierarchical model where group membership only influences the intercept, let $y_{is}$ be the result of pool $i$ taken from site $s$, where $s_1, \dots, s_K$ give the group memberhsip at levels $1,\dots, K$ of the hierarchical sampling scheme.
-Let $u_g^k$ be the group effect for group $g$ from level $k$ of the sampling scheme.
-Then our model is
-
-$y_{i s} |u_{s_k}^1,\dots,u_{s_k}^K, \beta, x_{i.},N_i \sim Bernoulli\left( 1-\left(1-logit^{-1}\left(\sum_k u^k_{s_k} + \sum_{j}{x_{ij} \beta_j}\right) \right)^{N_i}\right)$.
-
-$u^k_g \sim N(0,\sigma_k^2)$.
-
-## The PoolTestR package [Angus]
-The `PoolTestR` package has been designed to be a simple, fast, and user-friendly way to work with data from pooled samples of insects or other specimens.
-The package has four primary functions.
-`PoolPrev` estimates the prevalence of a marker based on the outcome of tests on pooled samples, calculating prevalence for many subgroups of the dataset if desired.
+The `PoolTestR` package has been designed to be a simple, user-friendly and extensible way to work with data from tests on pooled samples.
+The package has four primary functions for the estimation of prevalence, `PoolPrev`, `HierPoolPrev`, `PoolReg`, and `PoolRegBayes`.
+`PoolPrev` produces unadjusted estimates of prevalence of a marker based on the outcome of tests on pooled samples, optionally stratifying the dataset by one or more covariates.
 `HierPoolPrev` is like `PoolPrev`  but allows users to adjust prevalence estimates for hierarchical structure in sampling frames.
-`PoolReg` and `PoolRegBayes` fit mixed or fixed effect logistic regression models modified to account for the size of pools in either a frquentist or a bayesian framework.
-These allow users to identify temporal trends or variables (e.g.
-altitude, population density, interventions) associated with higher prevalence and to account for hierarchical sampling designs when estimating prevalence[^1].
-
-`PoolPrev` was designed to produce comparable results to the popular stand-alone application PoolScreen [ref Katholi1996] for familiarity to existing users of the software.
-However, PoolScreen requires many manual steps to import data, run analyses, and export results and lacks the flexibility of a general-purpose statistical environment provided by `R`.
-Using `PoolPrev` users can estimate the prevalence of a marker for their whole dataset or for different subgroups of their data (e.g.
-splitting data by vector species, location, season, or the combination of all variables) with a few lines of `R` code and simple syntax.
-This is achieved by utilising non-standard evaluation and tools for working with grouped datasets provided in the `R` package, `dplyr`.
-`HierPoolPrev` uses the same syntax as `PoolPrev` and returns results in a similar format, but allows users to adjust estimates of prevalence to account for the hierarchical sampling frame often employed in xenomonitoring studies.
-
- `PoolReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for fixed effects models and builds on the `glmer` function from the `lme4` package for mixed effect models.
-`PoolRegBayes` builds on the flexible non-linear modelling framework provided by the `brms` package to fit bayesian fixed and mixed effect regression models on data from pooled tests.
-By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of R.
+`PoolReg` and `PoolRegBayes` provide flexible and extensible frameworks to fit mixed or fixed effect regression models in either a frquentist or a bayesian framework, allowing users to identify temporal trends or variables associated with higher prevalence and to account for hierarchical sampling frames[^1].
+Table 1 provides an overview of the differences between the  four main functions.The following sections provide more details of these functions, Boxes X-Y provide example code, and Figures A-B compare the outputs of these functions when applied to a synthetic dataset.
 
@@
 
+| Function       | Example function call                                        | Are prevalence estimates stratified or adjusted for covariates?
+| Do the prevalence estimates account for the hierarchical sampling frame?
+| Bayesian / Frequentist | Output class  |
+| -------------- | ------------------------------------------------------------ | ------------------------------------------------------------ | ------------------------------------------------------------ | ---------------------- | ------------- |
+| `PoolPrev`     | `PoolPrev(Data, Result, NumInPool)`                          | Neither                                                      | No                                                           | Both                   | `tibble`      |
+|                | `PoolPrev(Data, Result, NumInPool, Cov1, Cov2)`              | Stratified                                                   | No                                                           | Both                   | `tibble`      |
+| `HierPoolPrev` | `PoolPrev(Data, Result, NumInPool, c('Level1', 'Level2'))`   | Neither                                                      | Yes                                                          | Bayesian               | `tibble`      |
+|                | `PoolPrev(Data, Result, NumInPool, c('Level1', 'Level2'), Cov1, Cov2)` | Stratified                                                   | Yes                                                          | Bayesian               | `tibble`      |
+| `PoolReg`      | `PoolReg(Result ~ Cov1 + Cov2, Data, NumInPool)`             | Adjusted                                                     | No                                                           | Frequentist            | `glmfit` \*   |
+|                | `PoolReg(Result ~ Cov1 + Cov2 + (1 | Level1 / Level2), Data, NumInPool)` | Adjusted                                                     | Yes                                                          | Frequentist            | `glmerMod` \* |
+| `PoolRegBayes` | `PoolRegBayes(Result ~ Cov1 + Cov2, Data, NumInPool)`        | Adjusted                                                     | No                                                           | Bayesian               | `brmsfit`\*   |
+|                | `PoolRegBayes(Result ~ Cov1 + Cov2 + (1 | Level1 / Level2), Data, NumInPool)` | Adjusted                                                     | Yes                                                          | Bayesian               | `brmsfit`\*   |
+
+**Table 1** A summary of the four main functions in PoolTestR, with example function calls applied to a hypothetical dataset called `Data` with columns: `NumInPool` (number of specimens in each pool), `Result` (1/0 result of test for each pool), `Cov1` and `Cov2` (two covariate variables),  and `Level1` and `Level2` (variables identifying sample location at two levels of the sampling frame hierarchy; e.g.
+village ID and site ID).
+\* Applying the function `getPrevalence` to these outputs extracts the prevalance for each unique combination of covariates and sampling sites into a list of one or more `tibble`s .
+
 ### PoolPrev
+
+`PoolPrev` was designed to produce comparable results to the popular stand-alone application PoolScreen [ref Katholi1996] for familiarity to existing users of the software.
+Stratifying a dataset and calculating prevalence for each subgroup of the data using PoolScreen requires many manual steps to import data, run analyses and export results.
+Using `PoolPrev` this can be achieved in a few lines of R code with a simple syntax.
+This is achieved by utilising non-standard evaluation and tools for working with grouped datasets provided in the `R` package, `dplyr`.
 
@@
 $Beta(0.5,0.5)$.
-Users can also optionally specify the prior probability that the marker of interested is entirely absent from the population, in which case `PoolPrev` also returns the probability of absence given the data.
+Users can also optionally specify the prior probability that the marker of interest is entirely absent from the population, in which case `PoolPrev` also returns the probability of absence given the data.
 As we assume the test performed on the pooled samples does not produce false positive or negatives, the probability of absence is always zero if any of the pools test positive.
@@
 Similarly, if all tests are negative the lower bound of the CrI is 0 and the lower bound is the 95% quantile of the posterior.
-The maximum likelihood estimate is calculated using the `optimizing` function from the `rstan` package.
 The uncertainty interval for the maximum likelihood estimate is calculated using the likelihood ratio method (i.e.
-a Wilk’s confidence interval) using the `uniroot` function from the `stats` package.
+a Wilk’s confidence interval).
 As with the Bayesian credible interval, the lower or upper bound of the confidence intervals are zero or one when all pools are negative or positive, respectively.
 
-The boxes below demonstrated the use of `PoolPrev` on a synthetic dataset.
-The synthetic dataset consists of 1000 pools from four different locations (A-D) over five years (0-4) of sampling.
-The ‘true’ prevalence in the initial year was 14% in locations A and D, 4% in location B and 1% in location C, and declined by approximately 18% each year.
+Box A demonstrates the use of `PoolPrev` on a synthetic dataset.
 
-```{r GenerateDataset, include=FALSE}
-library(dplyr)
-library(tidyr)
-### Create a synthetic dataset with 4 locations across 5 years,
-### where prevalence is declining
-NumPools <- 1000
-#Odds that a individual sample is positive in each location in the first year
-BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
-OddsRatioYear <- 0.8
-#Randomly distribute pools between the 4 locations and 5 years,
-#and chose random pool sizes between 10 and 25
-Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
-                   Year = sample(c(0:4), NumPools, replace = T),
-                   NumInPool = sample(10:25, NumPools, replace = T))
-#'True' odds/prevalence in each location
-Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
-Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
-#Simulate test results on pools
-Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
-Data <- Data %>% select(-TrueOdds,-TruePrev)
+```{r PoolPrevExample, warning=FALSE, cache=TRUE}
+#Looking at the first few rows of the synthetic dataset to see structure
+head(ExampleData)
+#Prevalence across the whole synthetic dataset (ignoring hierarchical sampling)
+Prevs <- PoolPrev(ExampleData, Result, NumInPool)
+#Prevalence for each Region (ignoring hierarchical sampling)
+PrevsRegion <- PoolPrev(ExampleData, Result, NumInPool, Region) 
+#Prevalence for each Year (ignoring hierarchical sampling)
+PrevsYear <- PoolPrev(ExampleData, Result, NumInPool, Year)
+#Prevalence for each combination of Region and Year (ignoring hierarchical sampling)
+PrevsYearRegion <- PoolPrev(ExampleData, Result, NumInPool, Region, Year)
+PrevsYearRegion
+
+#Prevalence for each Region and Year accounting for hierarchical sampling
+HierPrevsYearRegion <- HierPoolPrev(ExampleData, Result, NumInPool,
+																		c("Village", "Site"), Region, Year)
+#Similar to the above, but estimates prevalence, statifying down to village level
+HierPrevsYearRegionVillage <- HierPoolPrev(ExampleData, Result, NumInPool,
+																					 c("Site"), Region, Year, Village)
 ```
 
-```{r PoolPrevExample}
-#Looking at the first few rows of the synthetic dataset to see structure
-head(Data)
-#Prevalence across the whole synthetic dataset
-PoolPrev(Data, Result,NumInPool)
-#Prevalence at each location
-PoolPrev(Data, Result,NumInPool,Place)
-#Prevalence for each Year
-PoolPrev(Data, Result,NumInPool,Year)
-#Prevalence for each combination of location and Year
-PoolPrev(Data, Result,NumInPool,Place,Year)
+### HierPoolPrev
+Many xenomonitoring surveys involve a hierarchical sampling structure.
+For instance if one wishes to understand the prevalence in a particular village, one may place traps at a number of sites around the village.
+The vectors caught at each site can then be tested individually or in pools.
+However, as prevalence may vary from site to site, the result of tests on individuals vectors or pools from the same site cannot be considered independent.
+However, the function `PoolPrev` in our package and other software like PoolScreen assume that results of pools are independent.
+Estimating the prevalence for the whole village ignoring this dependance will result in over-confident (narrow) estimation intervals.
+To account for this dependance we can use a hierarchical model.
+
+`HeirPoolPrev` fits an intercept-only hierarchical generalised linear mixed model with a logistic link function.
+The syntax and outputs are very similar to `PoolPrev`.
+There is only one additional argument, `hierarchy`, describing the hierachical structure of the sampling frame.
+The output provides the Bayesian posterior mean and credible intervals for the prevalence, but unlike `PoolPrev` does not provide the maximum-likelihood estimate or likelihood ratio confidence intervals.
+As with `PoolPrev` users can specify variables that stratify the dataset into subgroups.
+If subgroups of the data are specified, estimation proceeds independantly for each subgroup.
+
+Box B demonstrates the use of `HierPoolPrev` on a synthetic dataset.
+
+### Regression - PoolReg and PoolReg Bayes
+Our package provides tools for mixed-effect regression models in both a frequentist and Bayesian framework.
+`PoolReg` fits a frequentist mixed- or fixed-effect generalised linear model that adjusts for the sizes of pools,  building on `glm` from the in the `stats` package for fixed-effect models and the `glmer` function from the `lme4` package for mixed-effect models.
+For a model with only fixed effects the output is a S3-object of class `glmfit`, while the output for a model with random effects is a S3-object of class `glmerMod` which supports that same methods (e.g.
+summary, predict, plot, confint) as any other object returned by the `glm` or `glmer` functions.
+`PoolRegBayes` provides functionality to perform the same analyses in a Bayesian framework and returns a `brmsfit` object.
+By building on these existing statistical packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of `R`.
+In addition, `PoolTestR` inlcudes the function `getPrevalence`, which provides a convenient way to extract estimates of prevalence from regression models fitted with `PoolReg` or `PoolRegBayes`.
+The function`getPrevalence`, is able to detect whether a model includes adjustements for hierarchical random/group effect terms, and automatically estimate prevalence at every level of the sampling hierarchy.
+
+Box B applies `PoolReg` and `PoolRegBayes`to the same synthetic dataset used to demonstrate `PoolPrev`, estimating the trend of decline in prevalence over time.
+
+```{r PoolLogitRegExample, warning=FALSE, cache=TRUE}
+# Logistic regression model - no adjustment for sampling frame hierarchy
+ModFreq <- PoolReg(Result ~ Region + Year,
+                   ExampleData, NumInPool)
+summary(ModFreq)
+# Logistic regression model - adjusting for sampling frame hierarchy
+ModFreqHier <- PoolReg(Result ~ Region + Year + (1|Village/Site),
+                       ExampleData, NumInPool)
+summary(ModFreqHier)
+```
+```{r PoolLogitRegBayesExample, eval = FALSE}
+# Same as above but in a Bayesian framework
+ModBayes <- PoolRegBayes(Result ~ Region + Year,
+                         ExampleData, NumInPool)
+ModBayesHier <- PoolRegBayes(Result ~ Region + Year + (1|Village/Site),
+                             ExampleData, NumInPool)
+```
+```{r HierExample, warning = FALSE, cache = TRUE}
+# A more complex model: estimate temporal trend for each village
+ModBayesHier2 <- PoolRegBayes(Result ~ Region + Year + (1 + Year|Village) + (1|Site),
+                              ExampleData, NumInPool)
+# We can use each of these models to estimate prevalence e.g.
+getPrevalence(ModFreq)
+# For hierarchical models getPrevalence returns prevalence at every level
+getPrevalence(ModBayesHier2)
+
+# We can also predict prevalence for new datapoints. For example, this projects
+# the temporal trend forward to estimate prevalence in region A in years 3-5.
+PredictData <- data.frame(Region = "A", Year = c(3,4,5))
+getPrevalence(ModFreq, newdata = PredictData)
 ```
 
-### PoolLogitReg
-Given a dataset containing the number of samples, the result of tests for each pool, potential dependent variables associated with each pool, and a formula defining the model, `PoolLogitReg` fits a logistic regression model that adjusts for the sizes of pools.
-The output is a S3-object of class `glm` which supports that same methods (e.g.
-summary, predict, plot, confint) as any other object returned by the `glm` function.
+### Comparison of methods on a synthetic dataset
 
-The boxes below apply `PoolLogitReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.
+`PoolTestR` provides a number of approaches to estimate prevalence: frequentist or Bayesian, stratifying or adjusting for covariates, adjusting for or ignoring hierarchical sampling frame (Table 1).
+We compare the approaches with another synthetic dataset with a realistic hierarchical sampling design.
 
-```{r PoolLogitRegExample}
-# Fit modified logistic regression model
-#The below two lines produce identical results and support all the same methods
-Reg <- PoolReg(Data,Result ~ Place + Year,
-                    NumInPool)
-Reg.glm <- glm(Result ~ Place + Year,
-               data = Data,
-               family = binomial(PoolLink(Data$NumInPool)))
-#View summary of model
-summary(Reg)
+We simulate samples taken from across three regions (A, B, and C) in which the vectors have a low (0.5\%), medium (2\%), and high (4\%) prevalence of the marker of interest.
+Within each region we choose ten villages, and within each of these villages we choose ten sites to place traps.
+We sample the same from the same locations once a year over three years (0, 1, and 2).
+Prevalence is not uniform within each region or over time.
+At baseline (year 0), prevalence varies between villages within each region around the mean for the region, and prevalence varies between sites within each village around the mean for the village.
+Consequently though the prevalence is different for each site, two sites within the same village are likely to have a more similar prevalence than two sites in different villages, or two sites in different regions.
+On average the prevalence is declining over time (odds ratio of 0.8 per year), however, the growth rate varies between villages.
+Consequently two sites in different villages with similar prevalence at baseline may have different prevalence by the third year, and prevalence may go up in some villages.
 
-#Estimate and confidence intervals for the base odds and odds ratios
-#These should be approx 0.16 for the intercept (i.e. Place A, Year 0),
-#0.25, 0.0625, and 1.0 for places B-D and 0.8 for Year
-exp(cbind(Estimate = coefficients(Reg), confint(Reg)))
+Each year the traps at each site catch a negative binomial number (mean 200, dispersion 5) of vectors.
+The catch size at each site and year is independent.
+Each year, the catches at each site are pooled into groups of 25 with an additional pool for any remainder (e.g.
+a catch of 53 vectors will be pooled into two pools of 25 and one pool of three).
+Each pool is tested for the marker of interest using a test with perfect sensitivity and specificity.
 
-#You can use the fitted model to predict the prevalence at other times
-#The times and places at which to predict the prevalence
-DataPredict <- expand.grid(Place = c("A","B","C","D"),Year = seq(2.2,2.8,by = 0.2))
-#Predicted prevalence
-DataPredict$PredictPrev <- plogis(predict(Reg, newdata = DataPredict)) 
-head(DataPredict)
+This synthetic dataset is provided with the package, and is the one used to illustrate the package in Boxes A and B.
+The predictions for each region and year, and for a sellection of villages are compared in Figure X and Y.
 
-# Note that predicting the response (i.e. the predicting the probability of
-# observing a positive test) using predict(type = "response") does not work
-# as expected on new data. Use the following instead:
+```{r AdditionalModelsForComparison, include = FALSE}
+PrevsYearRegionVillage <- PoolPrev(ExampleData, Result, NumInPool,Region,Year,Village)
 
-#Generate new random pool sizes for new data
-DataPredict$NumInPool <- sample(5:10,nrow(DataPredict),replace = T)
-DataPredict$PredictTestProb <- with(DataPredict, 1 - (1-PredictPrev)^NumInPool)
-head(DataPredict)
+ModFreqVillage <- PoolReg(Result ~ Region + Year + Village,
+                   ExampleData, NumInPool)
+
+HierPrevsYearRegion <- HierPoolPrev(ExampleData, Result, NumInPool, c("Village", "Site"), Region, Year)
+HierPrevsYearRegionVillage <- HierPoolPrev(ExampleData, Result, NumInPool, c("Site"), Region, Year, Village)
 ```
 
-Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolReg`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location.
-Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
-```{r Comparison, echo=FALSE}
+```{r HierComparisonRegion, echo=FALSE,warning = FALSE}
 library(ggplot2)
-PrevsYearPlace <- PoolPrev(Data, Result,NumInPool,Place,Year)
-PO <- PrevsYearPlace %>%
-  mutate(BaseOdds = BaseOdds[Place],
-         TrueOdds = BaseOdds * OddsRatioYear^(Year-min(Year)),
-         TruePrev = TrueOdds/(1+TrueOdds),
-         FreqPred = plogis(predict(Reg,newdata = PrevsYearPlace)),
-         FreqPredCILow = with(predict(Reg,
-                                      newdata = PrevsYearPlace,
-                                      se.fit =T),
-                              fit - se.fit * 1.96) %>% plogis,
-         FreqPredCIHigh = with(predict(Reg,
-                                       newdata = PrevsYearPlace,
-                                       se.fit =T),
-                               fit + se.fit * 1.96) %>% plogis
-  ) %>%
-  ggplot() +
-  geom_pointrange(aes(x = Year,
-                      color = Place,
-                      y = PrevMLE,
-                      ymin = CILow,
-                      ymax = CIHigh)) +
-  geom_line(aes(x = Year,
-                y= FreqPred,
-                color = Place)) +
-  geom_ribbon(aes(x = Year,
-                  ymin = FreqPredCILow,
-                  ymax = FreqPredCIHigh,
-                  fill = Place),
-              alpha = 0.3) +
-  geom_point(aes(x = Year, color = Place, y = TruePrev),
-             shape = 4,
-             size = 3) +
-  #scale_y_log10() +
-  ylab('Prevalence')
-PO
-```
+RegionPO <- rbind(TruePrev %>%
+                    select(Region, Year, Estimate = PrevalenceRegion) %>%
+                    mutate(CILow = NA, CIHigh = NA, Method = 'True') %>%
+                    unique(),
+                  PrevsYearRegion %>%
+                    select(Region, Year, Estimate = PrevMLE, CILow, CIHigh) %>%
+                    mutate(Method = 'PoolPrev (Frequentist)'),
+                  PrevsYearRegion %>%
+                    select(Region, Year, Estimate = PrevBayes, CILow = CrILow, CIHigh = CrIHigh) %>%
+                    mutate(Method = 'PoolPrev (Bayesian)'),
+                  getPrevalence(ModFreq)$PopulationEffects %>%
+                    mutate(Method = "PoolRegBayes"),
+                  getPrevalence(ModBayesHier2)$PopulationEffects %>%
+                    rename(CILow = CrILow, CIHigh = CrIHigh) %>%
+                    mutate(Method = "PoolRegBayes (Adjusted for hierarchy)"),
+                  HierPrevsYearRegion %>%
+                    select(Region, Year, Estimate = PrevBayes, CILow = CrILow, CIHigh = CrIHigh) %>%
+                    mutate(Method = "HierPoolPrev")) %>%
+  mutate(Region = factor(paste0("Region ", Region), levels = paste0("Region ",c("C","B","A"))),
+         Method = factor(Method, levels = c('PoolPrev (Frequentist)',
+                                            'PoolPrev (Bayesian)',
+                                            "HierPoolPrev",
+                                            "PoolRegBayes",
+                                            "PoolRegBayes (Adjusted for hierarchy)",
+                                            "True"))) %>%
+  unique() %>%
+  ggplot(aes(x = Year, y = Estimate,
+             ymin = CILow, ymax = CIHigh, shape = Method)) +
+  geom_pointrange(position = position_dodge(width = 0.3)) +
+  facet_grid(Region~.,scales = 'free_y') +
+  scale_y_log10() +
+  scale_x_continuous(breaks = 0:2) +
+  ylab("Prevalence") +
+  theme(text = element_text(size = 15),legend.position = "bottom") +
+  guides(shape = guide_legend(override.aes = list(linetype = 0)))
 
-## Testing
-A more realistic example:
-- 3 regions with prevalence:
-  - low (0.5%)
-  - medium (2%)
-  - high (4%) 
-- 10 villages in each region with prevalence:
-  - random normal distribted tight around region average, or 
-  - one hotspot and one coldspot village
-- 15 sites at each village.
-  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
-  - Mosquitos pooled into test-tubes of 25 + one pool with remainder
-
-```{r GenerateMoreRealisticDataset}
-RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
-NumRegions <- length(RegionPrevs)
-NumVillages <- 10 #Villages per Region
-NumSites <- 15 #Sites per village
-MeanCatch <- 200; #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
-DispersionCatch <- 5
-MaxPoolSize <- 25
-# Variability between villages and between sites in a given village.
-# We could probably increase these standard deviations to make the difference between the hierarchical and non-hierarchical models more stark
-VillageSD <- 1.0 
-SiteSD <- 0.5
-
-Data <- data.frame()
-for(R in names(RegionPrevs)){
-  for(V in 1:NumVillages){
-    #Difference of village prevalence from the region prevalence on log-odds scale
-    VillageDeviate <- rnorm(1,mean = 0, sd = VillageSD)
-    VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate)
-    for(S in 1:NumSites){
-      #Difference of site prevalence from the village prevalence on log-odds scale
-      SiteDeviate <- rnorm(1,mean = 0, sd = SiteSD)
-      SiteTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + SiteDeviate)
-      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes == 0 to guarantee at least one mossie
-      Catch <- 0
-      while(Catch<=0){
-        Catch <- rnbinom(1,mu = MeanCatch ,DispersionCatch)
-      }
-      #Split pools into as many of size MaxPoolSize as possible and the remainder in another small pool
-      NumBigPools <- Catch %/% MaxPoolSize
-      if(NumBigPools){
-        Data <- rbind(Data,
-                      data.frame(Region = R,
-                                 Village = paste(R,V,sep = "-"),
-                                 Site = paste(R,V,S,sep = "-"),
-                                 PoolSize = rep(MaxPoolSize,NumBigPools),
-                                 PrevalenceSite = SiteTruePrev,
-                                 PrevalenceVillage = VillageTruePrev,
-                                 PrevalenceRegion = RegionPrevs[[R]]))
-      }
-      SizeSmallPool <- Catch %% MaxPoolSize
-      if(SizeSmallPool){
-        Data <- rbind(Data,
-                      data.frame(Region = R,
-                                 Village = paste(R,V,sep = "-"),
-                                 Site = paste(R,V,S,sep = "-"),
-                                 PoolSize = SizeSmallPool,
-                                 PrevalenceSite = SiteTruePrev,
-                                 PrevalenceVillage = VillageTruePrev,
-                                 PrevalenceRegion = RegionPrevs[[R]]))
-      }
-    }
-  }
-}
-Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < (1-(1-PrevalenceSite)^PoolSize)))
-
-# Calculating prevalences at different levels ignoring hierarchical sampling structure
-PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
-PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
-PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)
-
-# Calulcating prevalences at different levels acknowledging hierarchical structure
-
-# Similar to above but in a regresison framework with Region as population
-# effect (aka fixed effect) and Village and Site as group effects (aka random
-# effect)
-
-HierPrevModel <- PoolRegBayes(Data, Result ~ Region + (1|Village/Site), PoolSize)
-HierPrevs <- getPrevalence(HierPrevModel) # Gett fitted prevalence at each level: Population Effects only (in this case this is region), Population Effects and Village, and population effects, village and site.
+RegionPO
 
@@
 
-```{r HierComparisonRegion, echo=FALSE}
-PlotDataRegion <- PrevRegion %>%
-  unique %>%
-  select(Region, PrevMLE, CILow, CIHigh) %>%
-  mutate(Method = 'Basic MLE') %>%
-  rename(Prev = PrevMLE) %>%
-  bind_rows(PrevRegion %>%
-              unique %>%
-              select(Region, PrevBayes, CrILow, CrIHigh) %>%
-              mutate(Method = 'Basic Bayes') %>%
-              rename(Prev = PrevBayes,
-                     CILow= CrILow,
-                     CIHigh = CrIHigh)) %>%
-  bind_rows(Data %>%
-              select(Region,PrevalenceRegion) %>%
-              unique %>%
-              mutate(Method = "True") %>%
-              rename(Prev = PrevalenceRegion)) %>%
-  bind_rows(HierPrevs$PopulationEffects %>%
-              mutate(Method = 'Heirarchical Bayes') %>%
-              rename(Prev = Estimate,
-                     CILow = CrILow,
-                     CIHigh = CrIHigh) %>%
-              select(Region, Prev, CILow, CIHigh, Method))
-
-PlotsRegion <- PlotDataRegion %>%
-  ggplot() +
-  geom_pointrange(aes(x = Method,
-                      color = Region,
-                      y = Prev,
-                      ymin = CILow,
-                      ymax = CIHigh,
-                      shape = Method)) +
-  facet_grid(~Region,scales = "free_x") +
-  #scale_y_continuous(labels=scales::percent) +
-  scale_y_log10(labels=scales::percent) +
-  scale_x_discrete(breaks = NULL)+
-  theme(axis.text.x = element_text(angle = 90)) +
-  ylab('Prevalence')
-PlotsRegion
+```{r HierComparisonVillage, echo=FALSE, warning = FALSE}
+VillagePO <- rbind(TruePrev %>%
+                     select(Region, Year, Village, Estimate = PrevalenceVillage) %>%
+                     mutate(CILow = NA, CIHigh = NA, Method = 'True'),
+                   PrevsYearRegionVillage %>%
+                     select(Region, Year, Village, Estimate = PrevMLE, CILow, CIHigh) %>%
+                     mutate(Method = 'PoolPrev (frequentist)'),
+                   PrevsYearRegionVillage %>%
+                     select(Region, Year, Village, Estimate = PrevBayes, CILow = CrILow, CIHigh = CrIHigh) %>%
+                     mutate(Method = 'PoolPrev (Bayesian)'),
+                   getPrevalence(ModFreqVillage)$PopulationEffects %>%
+                     mutate(Method = "PoolRegBayes",),
+                   getPrevalence(ModBayesHier2)$Village %>%
+                     rename(CILow = CrILow, CIHigh = CrIHigh) %>%
+                     mutate(Method = "PoolRegBayes (adjusted for hierarchy)"),
+                   HierPrevsYearRegionVillage %>%
+                     select(Region, Year, Village, Estimate = PrevBayes, CILow = CrILow, CIHigh = CrIHigh) %>%
+                     mutate(Method = "HierPoolPrev")) %>%
+  mutate(Region = factor(Region, levels = c("C","B","A")),
+         Method = factor(Method, levels = c('PoolPrev (frequentist)',
+                                            'PoolPrev (Bayesian)',
+                                            "HierPoolPrev",
+                                            "PoolRegBayes",
+                                            "PoolRegBayes (adjusted for hierarchy)",
+                                            "True"))) %>%
+  unique() %>%
+  mutate(VillageNum = stringr::str_split_fixed(Village, pattern = "-", n= 2)[,2]) %>%
+  subset(VillageNum %in% c(3,6,9)) %>%
+  mutate(Village = paste0("Village ",VillageNum),
+         Region = factor(paste0("Region ", Region), levels = paste0("Region ",c("C","B","A")))) %>%
+  ggplot(aes(x = Year, y = Estimate,
+             ymin = CILow, ymax = CIHigh, shape = Method)) +
+  geom_pointrange(position = position_dodge(width = 0.6)) +
+  facet_grid(Region~Village,scales = 'free_y') +
+  scale_y_log10() +
+  scale_x_continuous(breaks = 0:2) +
+  ylab("Prevalence") +
+  theme(text = element_text(size = 15),legend.position = "bottom") +
+  guides(shape = guide_legend(override.aes = list(linetype = 0)))
 
 ```
-```{r HierComparisonVillage, echo=FALSE}
-PlotDataVillage <- PrevVillage %>%
-  unique %>%
-  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
-  mutate(Method = 'Basic MLE') %>%
-  rename(Prev = PrevMLE) %>%
-  bind_rows(PrevVillage %>%
-              unique %>%
-              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
-              mutate(Method = 'Basic Bayes') %>%
-              rename(Prev = PrevBayes,
-                     CILow= CrILow,
-                     CIHigh = CrIHigh)) %>%
-  bind_rows(Data %>%
-              select(Region, Village,PrevalenceVillage) %>%
-              unique %>%
-              mutate(Method = "True") %>%
-              rename(Prev = PrevalenceVillage)) %>%
-  bind_rows(HierPrevs$Village %>%
-              mutate(Method = 'Heirarchical Bayes') %>%
-              rename(Prev = Estimate,
-                     CILow = CrILow,
-                     CIHigh = CrIHigh) %>%
-              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
-    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
-  subset(VillageNum %in% 1:5)
-
-PlotsVillage <- PlotDataVillage%>%
-  ggplot() +
-  geom_pointrange(aes(x = Village,
-                      color = Region,
-                      y = Prev,
-                      ymin = CILow,
-                      ymax = CIHigh,
-                      shape = Method),
-                  position = position_dodge(width = 0.8)) +
-  facet_grid(~Region,scales = "free_x") +
-  #scale_y_continuous(labels=scales::percent) +
-  scale_y_log10(labels=scales::percent) +
-  scale_x_discrete(breaks = NULL)+
-  theme(axis.text.x = element_text(angle = 90)) +
-  ylab('Prevalence')
-PlotsVillage
-
-```
